### 2023-12-01 Outputs/Presentation/bell_conference_slides.qmd
Repo set up

---
title: "Torrential Twitter: Climate Change, Female Politicians, and Harassment"
author: "Inessa De Angelis"
format:
  beamer:
    aspectratio: 169
    theme: Madrid
    colortheme: DarkBlue
    institute: The University of Toronto
    # toc: true
    # Table of contents not generating at the moment
editor: visual
header-includes: 
- \definecolor{DarkBlue}{rgb}{0.05, 0.15, 0.3}
- \setbeamercolor{structure}{fg=DarkBlue}
---

# Introduction

Hello!

------------------------------------------------------------------------

# Slide 2

### 2023-12-01 Scripts/00-simulate_data.R

@@ -1,0 +1,117 @@
+#### Preamble ####
+# Purpose: Simulates severity of harassment and type of account 
+# Author: Inessa De Angelis
+# Date: 1 December 2023
+# Contact: inessa.deangelis@mail.utoronto.ca
+# License: MIT
+
+#### Workspace setup ####
+library(tidyverse)
+library(janitor)
+
+#### Data expectations ####
+# Severity of harassment will vary on the 7-point scale from positive to hate speech 
+# Type of account will vary from Personal, Professional, Bots, Spammers, Anonymous, and Suspended/Deleted 
+# There will be a combination of verified and unverified Twitter users 
+# Personal accounts that send Tweets containing mid to high levels of harassment on the 7-point scale are likely to belong to people who support the Conservative Party or People's Party
+
+#### Simulate data ####
+## Simulate varying harassment on the 7-point scale, types of accounts on the 6-point scale, and whether a user is verified ##
+set.seed(16)
+num_people <- 4100
+varying_harassment <- tibble(
+  person = 1:num_people,
+  name_of_politician = sample(c("Chrystia Freeland", "Elizabeth May", "Laurel Collins"), size = num_people, replace = TRUE, prob = c(0.5, 0.3, 0.2)),
+  severity_of_harassment = sample(c("Positive", "Neutral", "Questioning authority", "Name-calling/Gender insults", "Vicious language", "Credible threats", "Hate speech"), size = num_people, replace = TRUE, prob = c(0.025, 0.1, 0.6, 0.2, 0.025, 0.025, 0.025)),
+  type_of_account = sample(c("Personal", "Professional", "Bots", "Spammers", "Anonymous", "Suspended/deleted"), size = num_people, replace = TRUE, prob = c(0.2, 0.025, 0.025, 0.4, 0.3, 0.050)),
+  verified = sample(c("No", "Yes"), size = num_people, replace = TRUE, prob = c(0.9, 0.1)))
+print(varying_harassment, n = 30)
+
+## Simulate personal accounts / conservative political views ##
+set.seed(16)
+personal_accounts <- tibble(
+  Account = 1:4100,
+  severity_of_harassment =
+    sample(x = c("Name-calling/Gender insults", "Vicious language", "Credible threats"), 
+           size = 4100, 
+           replace = TRUE, 
+           prob = c(0.5, 0.3, 0.2)), 
+  party_identification =
+    sample(x = c("Conservative", "People's Party"),
+           size = 4100,
+           replace = TRUE,
[…]

### 2023-12-01 Scripts/01-download_Chrystia_data.R

@@ -1,0 +1,2053 @@
+#### Preamble ####
+# Purpose: Download @cafreeland Tweets via voson.tcn
+# Author: Inessa De Angelis
+# Date: 4 October 2023
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+
+#### Workspace setup ####
+library(voson.tcn)
+library(tidyverse)
+
+#### Authentication ####
+token <- tcn_token(bearer = "ADD SECRET CREDENTIALS")
+
+#### Chrystia Freeland - key word "climate" and "environment", tweets from October 2022 - October 2023 ####
+# Collect tweets (this series is from May 13, 2022) #
+tweet_ids <-
+  c(
+    "https://twitter.com/cafreeland/status/1657437032073838594",
+    "1657468214794948614",
+    "1657525605347254272",
+    "1657531592166842370",
+    "1657512967888334848",
+    "1657469187621543936",
+    "1657446526904422406",
+    "1657470491265753088",
+    "1657749900736741376",
+    "1657465796946456578",
+    "1657497389798678534",
+    "1657465966324850688",
+    "1657778287836561408",
+    "1657723634495156224",
+    "1657604548821925888",
+    "1657476665755283460",
+    "1657498630662639617",
+    "1657505534507974658",
+    "1657509419805016064",
+    "1657523963818278914",
+    "1657523993640062976",
+    "1657551179977719809",
+    "1657551552679124992",
+    "1657586705455812608",
+    "1657752978022088707",
+    "1657478944751222788",
+    "1657558466217615360",
+    "1657595525808656385",
+    "1657458651722858497",
+    "1657563327428710401",
+    "1657557781178912768",
+    "1657513976912044033",
+    "1657517592863449095",
+    "1657474136745168899",
+    "1657487143114096643",
+    "1657484485594578948",
+    "1657766999047434242",
+    "1657734986684923906",
+    "1658121436085600256",
+    "1657535909548490754",
+    "1657848152236650496",
+    "1657468152035561472",
+    "1657533665461542914",
+    "1657457384514519041",
+    "1657800370025037824",
+    "1657726347014201345",
+    "1657564690669531136",
+    "1657546628062904320",
+    "1657602235507920897",
+    "1657494782095048705",
+    "1657474629081116672",
+    "1657456032002584578",
+    "1657451899560292354",
+    "1657844084382527489",
+    "1657785789911117826",
+    "1657553855901495298",
+    "1657486337933721600",
[…]

### 2023-12-01 Scripts/01-download_Elizabeth_data.R

@@ -1,0 +1,1624 @@
+#### Preamble ####
+# Purpose: Download @elizabethmay Tweets via voson.tcn
+# Author: Inessa De Angelis
+# Date: 4 October 2023
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+
+#### Workspace setup ####
+library(voson.tcn)
+library(tidyverse)
+
+#### Authentication ####
+token <- tcn_token(bearer = "ADD SECRET CREDENTIALS")
+
+#### Elizabeth May - key word "climate", tweets from October 2022 - October 2023 ####
+# Collect tweets #
+tweet_ids <-
+  c(
+    "https://twitter.com/ElizabethMay/status/1700787904119992692",
+    "1700834322453073949",
+    "1700831757996531996",
+    "1700845024718594507",
+    "1700825646359097434",
+    "1700793175068275062",
+    "1700872590565503379",
+    "1700876914993561705",
+    "1700899727250805232",
+    "1700860101613977798",
+    "1700980753155412104",
+    "1700957486826615119"
+  )
+
+liz_tweets_sep10 <- tcn_threads(tweet_ids, token)
+
+print(liz_tweets_sep10)
+
+as_tibble(liz_tweets_sep10[["tweets"]])
+
+as_tibble(liz_tweets_sep10[["users"]])
+
+write_csv(x = liz_tweets_sep10[["users"]],
+          file = "raw_liz_tweets_sep10.csv")
+
+write_csv(x = liz_tweets_sep10[["tweets"]],
+          file = "raw_liz_tweets_sep10_2.csv")
+
+# Collect tweets #
+tweet_ids <-
+  c(
+    "https://twitter.com/ElizabethMay/status/1684608277035057152",
+    "1684817729675780096",
+    "1684962561442160648",
+    "1684746692371910656",
+    "1684626716616978432",
+    "1684674776466665474",
+    "1684714960897597440",
+    "1684614033159094286",
+    "1684667295493214209",
+    "1684704429767790593",
+    "1684708291765534720",
+    "1684907521734250496",
+    "1684766184431058944",
+    "1684735271181422592",
+    "1684931737636507648",
+    "1685081923712946176",
+    "1684668519680479232",
+    "1684676561880956928",
+    "1684718778993819648",
+    "1684685918408749065",
+    "1684612452791803904",
+    "1684671239434952704",
+    "1684807319744626689",
[…]

### 2023-12-01 Scripts/01-download_Laurel_data.R

@@ -1,0 +1,1213 @@
+#### Preamble ####
+# Purpose: Download @laurel_bc Tweets via voson.tcn
+# Author: Inessa De Angelis
+# Date: 4 October 2023
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+
+#### Workspace setup ####
+library(voson.tcn)
+library(tidyverse)
+
+#### Authentication ####
+token <- tcn_token(bearer = "ADD SECRET CREDENTIALS")
+
+#### Laurel Collins - key word "climate", tweets from October 2022 - October 2023 #####
+# Collect tweets #
+tweet_ids <-
+  c(
+    "https://twitter.com/Laurel_BC/status/1709351908400562457",
+    "1709596434259984455",
+    "1710320459806331123"
+  )
+
+laurel_tweets_oct_3 <- tcn_threads(tweet_ids, token)
+
+print(laurel_tweets_oct_3)
+
+as_tibble(laurel_tweets_oct_3[["tweets"]])
+
+as_tibble(laurel_tweets_oct_3[["users"]])
+
+write_csv(x = laurel_tweets_oct_3[["users"]],
+          file = "raw_laurel_tweets_oct_3.csv")
+
+write_csv(x = laurel_tweets_oct_3[["tweets"]],
+          file = "raw_laurel_tweets_oct_3_2.csv")
+
+# Collect tweets #
+tweet_ids <-
+  c(
+    "https://twitter.com/Laurel_BC/status/1692249500797264227",
+    "1692249755882319980",
+    "1692575263790448735",
+    "1692412069466005800",
+    "1692569627749224907",
+    "1692384447012708395",
+    "1692365254309687385",
+    "1692480797549494510",
+    "1692555897036243248",
+    "1692569432453775840",
+    "1692572482786734501",
+    "1692267562552418795",
+    "1692572723694780590",
+    "1692504561028661636",
+    "1692581199162818798",
+    "1692359970564780112",
+    "1692560268046545126",
+    "1692382056565940401",
+    "1692570379166925164",
+    "1692367027581984927",
+    "1692409270170706038",
+    "1692610187046146396",
+    "1692565656992936098",
+    "1692544063390830945",
+    "1692562203059142697",
+    "1692695063166439861",
+    "1692562611609407771",
+    "1692566623193084261",
+    "1692563780847141003",
+    "1692563805144772941",
+    "1692934016054259883",
+    "1692562613962416605",
[…]

### 2023-12-01 Scripts/02-clean_raw_Chrystia_data.R

@@ -1,0 +1,544 @@
+#### Preamble ####
+# Purpose: Clean raw @cafreeland Tweets 
+# Author: Inessa De Angelis
+# Date: 30 October 2023
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites
+  # 01-download_Chrystia_data.R
+
+#### Workspace setup ####
+library(tidyverse)
+library(janitor)
+
+##### STEP 1 - eliminate extra columns & combine user info and tweet text datasets #####
+### Clean February 25 Tweets ###
+# Read in Tweets #
+raw_chrystia_tweets_feb_25 <-
+  read_csv("Inputs/Data/Chrystia/raw_chrystia_tweets_feb_25.csv")
+show_col_types = FALSE
+
+raw_chrystia_tweets_feb_25_2 <-
+  read_csv("Inputs/Data/Chrystia/raw_chrystia_tweets_feb_25_2.csv")
+show_col_types = FALSE
+
+# Cleaning: select columns of interest #
+trial_chrystia_feb_25 =
+  raw_chrystia_tweets_feb_25 |>
+  select(
+    profile.name,
+    profile.verified,
+    profile.url,
+    profile.public_metrics.followers_count,
+    profile.public_metrics.following_count,
+    profile.description,
+    profile.username,
+    profile.profile_image_url,
+    profile.location,
+    user_id
+  )
+trial_chrystia_feb_25
+
+trial_chrystia_feb_25_2 =
+  raw_chrystia_tweets_feb_25_2 |>
+  select(text,
+         author_id,
+         tweet_id,
+         conversation_id)
+trial_chrystia_feb_25_2
+
+combined_chrystia_tweets_feb_25 <-
+  cbind(trial_chrystia_feb_25, trial_chrystia_feb_25_2)
+
+# Save dataset #
+write_csv(x = combined_chrystia_tweets_feb_25, file = "Outputs/Data/Chrystia/combined_chrystia_tweets_feb_25.csv")
+
+### Clean January 18 Tweets ###
+# Read in Tweets #
+raw_chrystia_tweets_jan_18 <-
+  read_csv("Inputs/Data/Chrystia/raw_chrystia_tweets_jan_18.csv")
+show_col_types = FALSE
+
+raw_chrystia_tweets_jan_18_2 <-
+  read_csv("Inputs/Data/Chrystia/raw_chrystia_tweets_jan_18_2.csv")
+show_col_types = FALSE
+
[…]

### 2023-12-01 Scripts/02-clean_raw_Elizabeth_data.R

@@ -1,0 +1,1467 @@
+#### Preamble ####
+# Purpose: Clean raw @elizabethmay Tweets 
+# Author: Inessa De Angelis
+# Date: 23 October 2023
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites
+  # 01-download_Elizabeth_data.R
+
+#### Workspace setup ####
+library(tidyverse)
+library(janitor)
+
+##### STEP 1 - eliminate extra columns & combine user info and tweet text datasets #####
+### Clean December 17 Tweets ###
+# Read in Tweets #
+raw_liz_tweets_dec_17 <-
+  read_csv("Inputs/Data/Elizabeth/raw_liz_tweets_dec_17.csv")
+show_col_types = FALSE
+
+raw_liz_tweets_dec_17_2 <-
+  read_csv("Inputs/Data/Elizabeth/raw_liz_tweets_dec_17_2.csv")
+show_col_types = FALSE
+
+# Cleaning: select columns of interest #
+trial_liz_dec_17 =
+  raw_liz_tweets_dec_17 |>
+  select(
+    profile.name,
+    profile.verified,
+    profile.url,
+    profile.public_metrics.followers_count,
+    profile.public_metrics.following_count,
+    profile.description,
+    profile.username,
+    profile.profile_image_url,
+    profile.location,
+    user_id
+  )
+trial_liz_dec_17
+
+trial_liz_dec_17_2 =
+  raw_liz_tweets_dec_17_2 |>
+  select(text,
+         author_id,
+         tweet_id,
+         conversation_id)
+trial_liz_dec_17_2
+
+combined_liz_tweets_dec_17 <-
+  cbind(trial_liz_dec_17, trial_liz_dec_17_2)
+
+# Save dataset #
+write_csv(x = combined_liz_tweets_dec_17, file = "Outputs/Data/Elizabeth/combined_liz_tweets_dec_17.csv")
+
+### Clean February 13 Tweets ###
+# Read in Tweets #
+raw_liz_tweets_feb_13 <-
+  read_csv("Inputs/Data/Elizabeth/raw_liz_tweets_feb_13.csv")
+show_col_types = FALSE
+
+raw_liz_tweets_feb_13_2 <-
+  read_csv("Inputs/Data/Elizabeth/raw_liz_tweets_feb_13_2.csv")
+show_col_types = FALSE
+
+# Cleaning: select columns of interest #
[…]

### 2023-12-01 Scripts/02-clean_raw_Laurel_data.R

@@ -1,0 +1,1098 @@
+#### Preamble ####
+# Purpose: Multi-step cleaning of @laurel_bc Tweets
+# Author: Inessa De Angelis
+# Date: 18 October 2023
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites
+  # 01-download_Laurel_data.R
+
+#### Workspace setup ####
+library(tidyverse)
+library(janitor)
+
+##### STEP 1 - eliminate extra columns & combine user info and tweet text datasets #####
+### Clean April 12 Tweets ###
+# Read in Tweets #
+raw_laurel_tweets_apr_12 <-
+  read_csv("Inputs/Data/Laurel/raw_laurel_tweets_apr_12.csv")
+show_col_types = FALSE
+
+raw_laurel_tweets_apr_12_2 <-
+  read_csv("Inputs/Data/Laurel/raw_laurel_tweets_apr_12_2.csv")
+show_col_types = FALSE 
+
+# Cleaning: select columns of interest #
+trial_laurel_apr_12 =
+  raw_laurel_tweets_apr_12 |>
+  select(
+    profile.name,
+    profile.verified,
+    profile.url,
+    profile.public_metrics.followers_count,
+    profile.public_metrics.following_count,
+    profile.description,
+    profile.username,
+    profile.profile_image_url,
+    profile.location,
+    user_id
+  )
+trial_laurel_apr_12
+
+trial_laurel_apr_12_2 =
+  raw_laurel_tweets_apr_12_2 |>
+  select(
+    text,
+    author_id,
+    tweet_id,
+    conversation_id
+    )
+trial_laurel_apr_12_2
+
+combined_laurel_tweets_apr_12 <- cbind(trial_laurel_apr_12, trial_laurel_apr_12_2)
+
+# Save dataset #
+write_csv(x = combined_laurel_tweets_apr_12, file = "Outputs/Data/Laurel/combined_laurel_tweets_apr_12.csv")
+
+### Clean April 21 Tweets ###
+# Read in Tweets #
+raw_laurel_tweets_apr_21 <-
+  read_csv("Inputs/Data/Laurel/raw_laurel_tweets_apr_21.csv")
+show_col_types = FALSE
+
+raw_laurel_tweets_apr_21_2 <-
+  read_csv("Inputs/Data/Laurel/raw_laurel_tweets_apr_21_2.csv")
+show_col_types = FALSE 
+
[…]

### 2023-12-01 Scripts/03-test_raw_Chrystia_data.R

@@ -1,0 +1,43 @@
+#### Preamble ####
+# Purpose: Tests raw @cafreeland Tweets 
+# Author: Inessa De Angelis
+# Date: 31 October 2023
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites
+  # 02-clean_raw_Chrystia_data.R
+
+#### Workspace setup ####
+library(tidyverse)
+library(validate)
+
+#### Read in cleaned Tweets ####
+cleaned_chrystia_tweets <-
+  read_csv("Outputs/Data/Chrystia/final_cleaned_chrystia_tweets.csv")
+show_col_types = FALSE
+
+#### Test ####
+# Check for type of variables #
+rules <- validator(
+  is.character(Name),
+  is.character(Verified),
+  is.character(URL),
+  is.numeric(Followers),
+  is.numeric(Following),
+  is.character(Bio),
+  is.character(Username),
+  is.character(Profile_picture),
+  is.function(location),
+  is.character(Text),
+  is.numeric(User_id),
+  is.numeric(Conversation_id),
+  Verified %in% c("No", "Yes", "other")
+)
+
+out <-
+  confront(cleaned_chrystia_tweets, rules)
+
+summary(out)
+
+# Check number of rows is correct #
+nrow(cleaned_chrystia_tweets) == 2408

### 2023-12-01 Scripts/03-test_raw_Elizabeth_data.R

@@ -1,0 +1,43 @@
+#### Preamble ####
+# Purpose: Tests raw @elizabethmay Tweets 
+# Author: Inessa De Angelis
+# Date: 30 October 2023
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites
+  # 02-clean_raw_Elizabeth_data.R
+
+#### Workspace setup ####
+library(tidyverse)
+library(validate)
+
+#### Read in cleaned Tweets ####
+cleaned_liz_tweets <-
+  read_csv("Outputs/Data/Elizabeth/final_cleaned_liz_tweets.csv")
+show_col_types = FALSE
+
+#### Test ####
+# Check for type of variables #
+rules <- validator(
+  is.character(Name),
+  is.character(Verified),
+  is.character(URL),
+  is.numeric(Followers),
+  is.numeric(Following),
+  is.character(Bio),
+  is.character(Username),
+  is.character(Profile_picture),
+  is.function(location),
+  is.character(Text),
+  is.numeric(User_id),
+  is.numeric(Conversation_id),
+  Verified %in% c("No", "Yes", "other")
+)
+
+out <-
+  confront(cleaned_liz_tweets, rules)
+
+summary(out)
+
+# Check number of rows is correct #
+nrow(cleaned_liz_tweets) == 1059

### 2023-12-01 Scripts/03-test_raw_Laurel_data.R

@@ -1,0 +1,43 @@
+#### Preamble ####
+# Purpose: Tests raw @Laurel_bc Tweets before manual coding
+# Author: Inessa De Angelis
+# Date: 23 October 2023
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites
+  # 02-clean_raw_Laurel_data.R
+
+#### Workspace setup ####
+library(tidyverse)
+library(validate)
+
+#### Read in cleaned Tweets ####
+cleaned_laurel_tweets <-
+  read_csv("Outputs/Data/Laurel/final_cleaned_laurel_tweets.csv")
+show_col_types = FALSE
+
+#### Test ####
+# Check for type of variables #
+rules <- validator(
+  is.character(Name),
+  is.character(Verified),
+  is.character(URL),
+  is.numeric(Followers),
+  is.numeric(Following),
+  is.character(Bio),
+  is.character(Username),
+  is.character(Profile_picture),
+  is.function(location),
+  is.character(Text),
+  is.numeric(User_id),
+  is.numeric(Conversation_id),
+  Verified %in% c("No", "Yes", "other")
+)
+
+out <-
+  confront(cleaned_laurel_tweets, rules)
+
+summary(out)
+
+# Check number of rows is correct #
+nrow(cleaned_laurel_tweets) == 682

### 2023-12-01 Scripts/04-clean_coded_tweets.R

@@ -1,0 +1,76 @@
+#### Preamble ####
+# Purpose: Cleans Tweets for all three female politicians that were manually coded
+# Author: Inessa De Angelis
+# Date: 15 November 2023
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites
+  # Must manually code the Tweets first
+
+#### Workspace setup ####
+library(tidyverse)
+library(janitor)
+
+#### Read in the raw coded Tweets ####
+raw_coded_tweets <- read_csv("Outputs/Data/coding_form_responses.csv", show_col_types = FALSE)
+
+#### Cleaning ####
+# Name organization #
+cleaned_coded_tweets <-
+  clean_names(raw_coded_tweets)
+
+# Select columns of interest #
+cleaned_coded_tweets <-
+  cleaned_coded_tweets |>
+  select(
+    name_of_politician,
+    name,
+    verified,
+    bio,
+    username,
+    tweet_text,
+    severity_of_harassment,
+    type_of_account
+  )
+head(cleaned_coded_tweets)  
+
+# Add ID column #
+finalized_cleaned_tweets <-
+  cleaned_coded_tweets |>
+  mutate(ID = c(1:2564),
+         .before = name_of_politician) |>
+  select(ID, name_of_politician, name, verified, bio, username, tweet_text, severity_of_harassment, type_of_account)
+head(finalized_cleaned_tweets)
+
+# Case Match #
+finalized_cleaned_tweets <-
+  finalized_cleaned_tweets |>
+  mutate("severity_of_harassment" = case_when(
+    severity_of_harassment == 1 ~ "Positive",
+    severity_of_harassment == 2 ~ "Neutral",
+    severity_of_harassment == 3 ~ "Questioning Authority",
+    severity_of_harassment == 4 ~ "Name-calling/Gender insults",
+    severity_of_harassment == 5 ~ "Vicious language",
+    severity_of_harassment == 6 ~ "Credible threats",
+    severity_of_harassment == 7 ~ "Hate speech",
+  )) |>
+  mutate("type_of_account" = case_when(
+    type_of_account == 1 ~ "Personal",
+    type_of_account == 2 ~ "Professional",
+    type_of_account == 3 ~ "Bots",
+    type_of_account == 4 ~ "Spammers",
+    type_of_account == 5 ~ "Anonymous",
+    type_of_account == 6 ~ "Suspended/deleted",
+  )) |>
[…]

### 2023-12-01 Scripts/05-test_cleaned_coded_tweets.R

@@ -1,0 +1,31 @@
+#### Preamble ####
+# Purpose: Tests the cleaned, coded Tweets
+# Author: Inessa De Angelis
+# Date: 15 November 2023
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites
+# 01-clean_coded_tweets.R
+
+#### Workspace setup ####
+library(testthat)
+
+# Read in data #
+finalized_cleaned_tweets <- read_csv("Outputs/Data/finalized_cleaned_tweets.csv", show_col_types = FALSE)
+
+#### Testing ####
+test_that("check class" , {
+  expect_type(finalized_cleaned_tweets$ID, "integer")
+  expect_type(finalized_cleaned_tweets$name_of_politician, "character")
+  expect_type(finalized_cleaned_tweets$name, "character")
+  expect_type(finalized_cleaned_tweets$verified, "character")
+  expect_type(finalized_cleaned_tweets$bio, "character")
+  expect_type(finalized_cleaned_tweets$username, "character")
+  expect_type(finalized_cleaned_tweets$tweet_text, "character")
+  expect_type(finalized_cleaned_tweets$severity_of_harassment, "character")
+  expect_type(finalized_cleaned_tweets$type_of_account, "character")
+})
+
+test_that("Check number of observations is correct", {
+  expect_equal(nrow(finalized_cleaned_tweets), 4100)
+})

### 2023-12-01 Scripts/06-model.R

@@ -1,0 +1,56 @@
+#### Preamble ####
+# Purpose: Models
+# Author: Inessa De Angelis
+# Date: 15 November 2023
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites
+  # 04-clean_coded_tweets.R
+  # 05-test_cleaned_coded_tweets.R
+
+#### Workspace setup ####
+library(tidyverse)
+library(rstanarm)
+library(modelsummary)
+library(marginaleffects)
+library(bayesplot)
+library(tidybayes)
+
+# Read in data #
+finalized_cleaned_tweets <- read_csv("Outputs/Data/finalized_cleaned_tweets.csv", show_col_types = FALSE)
+
+#### Prepare data to model ####
+## Create analysis data with severity of harassment factored ##
+analysis_data_binary <-
+  finalized_cleaned_tweets |>
+  select(severity_of_harassment, type_of_account, verified, name_of_politician) |>
+  mutate(harassment_binary = if_else(severity_of_harassment == "Positive" | severity_of_harassment == "Neutral",
+                                     0,
+                                     1)) 
+analysis_data_binary
+
+## Test data ##
+class(analysis_data_binary$severity_of_harassment) == "character"
+class(analysis_data_binary$type_of_account) == "character"
+class(analysis_data_binary$verified) == "character"
+class(analysis_data_binary$name_of_politician) == "character"
+class(analysis_data_binary$harassment_binary) == "numeric"
+nrow(analysis_data_binary) == 4100
+
+#### Make Bayesian hierarchical model ####
+harassment_model <-
+  stan_glmer(
+    harassment_binary ~ (1 | type_of_account) + (1 | name_of_politician) + (1 | verified),
+    data = analysis_data_binary,
+    family = binomial(link = "logit"),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    seed = 16
+  )
+verified_model
+
+## Save model ##
+saveRDS(harassment_model, "Outputs//Model/harassment_model.rds")
+
+## Summary ##
+summary(harassment_model)

### 2024-01-05 Scripts/05-test_cleaned_coded_tweets.R
Codebook

@@ -5,7 +5,7 @@
 # Contact: inessa.deangelis@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites
-# 01-clean_coded_tweets.R
+  # 01-clean_coded_tweets.R
 
 #### Workspace setup ####
 library(testthat)

### 2024-01-06 Outputs/Presentation/bell_conference_slides.qmd
slides and files

@@
 title: "Torrential Twitter: Climate Change, Female Politicians, and Harassment"
-author: "Inessa De Angelis"
+author: 
+  name: "Inessa De Angelis"
+  email: "Inessa.DeAngelis@mail.utoronto.ca"
 format:
-  beamer:
-    aspectratio: 169
-    theme: Madrid
-    colortheme: DarkBlue
-    institute: The University of Toronto
-    # toc: true
-    # Table of contents not generating at the moment
-editor: visual
-header-includes: 
-- \definecolor{DarkBlue}{rgb}{0.05, 0.15, 0.3}
-- \setbeamercolor{structure}{fg=DarkBlue}
+  revealjs
+title-slide-attributes: 
+  data-background-color: "#CBD6BE"
 ---
 
-# Introduction
+## Background {background-color="#CBD6BE"}
+- Harassment on Twitter is well-documented
 
-Hello!
+```{r}
+library(tidyverse)
+library(knitr)
+library(kableExtra)
+library(ggplot2)
+library(formattable)
+library(here)
 
-------------------------------------------------------------------------
+# Read in the data #
+finalized_cleaned_tweets_anon <- read_csv(here::here("Outputs/Data/finalized_cleaned_tweets_anon.csv"))
+show_col_types = FALSE
 
-# Slide 2
+#| message: false
+#| eval: true
+#| echo: false
+#| label: tbl-breakdown
+#| tbl-cap: Number of Tweets and their overall percentage of the sample by female politician following the data cleaning process
+
+finalized_cleaned_tweets_anon |>
+  group_by(name_of_politician) |>
+  count() |>
+  ungroup() |>
+  mutate(pct = paste0(round((n / sum(n)) * 100), "%")) |>
+  arrange(match(name_of_politician, c('Chrystia Freeland', 'Elizabeth May', 'Laurel Collins'))) |>
+  kable(
+    col.names = c("Name of Politician", "Number of Replies", "Percentage"),
+    booktabs = TRUE,
+  )
+
+````

### 2024-01-06 Scripts/04-clean_coded_tweets.R

@@ -65,12 +65,8 @@ finalized_cleaned_tweets <-
   select(ID, name_of_politician, name, verified, bio, username, tweet_text, severity_of_harassment, type_of_account)
 finalized_cleaned_tweets
 
-#### Save cleaned data in CSV file format ####
+#### Save cleaned data ####
 write_csv(
   x = finalized_cleaned_tweets,
-  file = "Outputs//Data/finalized_cleaned_tweets.csv"
+  file = "Outputs/Data/finalized_cleaned_tweets.csv"
 )
-
-finalized_cleaned_tweets |>
-  group_by(type_of_account) |>
-  count()

### 2024-01-06 Scripts/06-model.R

@@ -35,7 +35,7 @@ class(analysis_data_binary$type_of_account) == "character"
 class(analysis_data_binary$verified) == "character"
 class(analysis_data_binary$name_of_politician) == "character"
 class(analysis_data_binary$harassment_binary) == "numeric"
-nrow(analysis_data_binary) == 4100
+nrow(analysis_data_binary) == 4139
 
 #### Make Bayesian hierarchical model ####
 harassment_model <-
@@ -50,7 +50,7 @@ harassment_model <-
 verified_model
 
 ## Save model ##
-saveRDS(harassment_model, "Outputs//Model/harassment_model.rds")
+saveRDS(harassment_model, "Outputs/Model/harassment_model.rds")
 
 ## Summary ##
 summary(harassment_model)

### 2024-01-09 Outputs/Paper/Bell_Conference_Paper.qmd
Paper, script, and ReadMe updates

---
title: "Torrential Twitter: Climate Change, Female Politicians, and Harassment"
author: "Inessa De Angelis^[Faculty of Information, University of Toronto, Inessa.DeAngelis@mail.utoronto.ca]"
thanks: "Code and select data available at: https://github.com/InessaDeAngelis/torrential_twitter_bell_conf "
date: "today"
date-format: "long"
abstract: "Women in politics face considerable harassment. Known as “gendertrolling,” this harassment is part of a global trend of violence against women in politics. There are many significant previously documented cases of gendertrolling on public social media platforms such as Twitter. Framed through the theory of deliberative democracy, this study conducts quantitative content analysis on the replies received by three female politicians in Canada when Tweeting about climate change and the environment. These politicians are Deputy Prime Minister Chrystia Freeland (from the Liberal Party), Elizabeth May (co-Leader of the Green Party), and Laurel Collins (from the New Democratic Party). I then built a Bayesian hierarchical model to investigate the relationship between the severity of harassment and the type of account that a user has. The majority of replies contain some form of harassment, often questioning authority or name-calling/gender insults, and come from users that have spam or anonymous accounts. *This paper contains language and themes that some readers may find offensive.*"
format: pdf
toc: true
number-sections: true
bibliography: conference_references.bib
csl: apa.csl
---

```{r}
#| include: false
#| warning: false
#| message: false

#### Workspace set-up ####
# Load packages #
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggplot2)
library(formattable)
library(marginaleffects)
library(modelsummary)
library(flextable)

# Read in the data #
finalized_cleaned_tweets <- read_csv(here::here("Outputs/Data/finalized_cleaned_tweets.csv"))
show_col_types = FALSE

# Create specific datasets #
bio_data_PPC <-
finalized_cleaned_tweets |>
  select(ID,
  name_of_politician,
  bio,
  severity_of_harassment, 
  type_of_account
  ) |>
  filter(grepl('PPC', bio))

bio_data_CPC <-
finalized_cleaned_tweets |>
  select(ID,
  name_of_politician,
  bio,
  severity_of_harassment, 
  type_of_account
  ) |>
  filter(grepl('conservative', bio))

bio_data_CPC2 <-
finalized_cleaned_tweets |>
  select(ID,
  name_of_politician,
  bio,
  severity_of_harassment, 
  type_of_account
  ) |>
  filter(grepl('Conservative', bio))

bio_data_MAGA <-
finalized_cleaned_tweets |>
  select(ID,
  name_of_politician,
  bio,
  severity_of_harassment, 
  type_of_account
  ) |>
  filter(grepl('MAGA', bio))

bio_data_Trump <-
finalized_cleaned_tweets |>
  select(ID,
  name_of_politician,
  bio,
  severity_of_harassment, 
  type_of_account
  ) |>
  filter(grepl('Trump', bio))

bio_data_Trudeau <-
finalized_cleaned_tweets |>
  select(ID,
  name_of_politician,
  bio,
  severity_of_harassment, 
  type_of_account
  ) |>
  filter(grepl('Trudeau', bio))

bio_data_apples <-
finalized_cleaned_tweets |>
  select(ID,
  name,
  name_of_politician,
  bio,
  severity_of_harassment, 
  type_of_account
  ) |>
  filter(grepl('🍎', bio))

name_data_apples <-
finalized_cleaned_tweets |>
  select(ID,
  name,
  name_of_politician,
  bio,
  severity_of_harassment, 
  type_of_account
  ) |>
  filter(grepl('🍎', name))

# Merge together all bio datasets #
combined_bio_data <- rbind(bio_data_CPC, bio_data_MAGA, bio_data_PPC, bio_data_Trudeau, bio_data_CPC2, bio_data_Trump)
combined_bio_data

combined_apple_data <- rbind(bio_data_apples, name_data_apples)
combined_apple_data
```

\newpage

# Introduction

"F\*CK OFF WITH YOUR CLIMATE SCAM .. nazi traitor b!tch," reads a reply sent to a Tweet about climate change that originated on the account of Canada's Deputy Prime Minister (DPM) and Minister of Finance, the Honourable Chrystia Freeland. For DPM Freeland and women across all political parties and levels of government in Canada and other democratic nations, coping with online and offline harassment is a reality of serving as an elected official [@southern; @silencingwomen]. Known as "gendertrolling," this harassment is part of a global trend of violence against women [@mantilla2013; @wagner]. Gender-based harassment on Twitter is well documented in academic literature and inexplicably pro-environmental behaviors are often viewed as "feminine" [@Citron; @mediatingmisogyny; @Anshelm]. Female politicians who adopt strong policy stances are more likely to face online misogyny and harassment because it is not consistent with existing gender stereotypes and notions of power and poses a threat to male climate deniers [@courtemanche; @rheault; @degeus].

To gain a deeper understanding of the intersection of climate change denialism and online gendered-harassment faced by Canadian female politicians, I measure the severity of harassment DPM and MP for University--Rosedale, Hon. Chrystia Freeland (from the Liberal Party), MP for Saanich--Gulf Islands, Elizabeth May (Co-Leader of the Green Party), and MP for Victoria, Laurel Collins (from the New Democratic Party) receive specifically when Tweeting about climate change and environmental policy on a seven-point scale and investigate the types of accounts behind the Tweets on a six-point scale. After manually coding Tweets to determine the severity of harassment and type of account, I then built a Bayesian hierarchical model to explore the relationship between the type of account, whether a user was verified through Twitter's subscription program, and which female politician the reply was directed toward to see whether certain combinations of these variables are more likely to lead to a reply which contains harassment. It is hypothesized that evidence of harassment will be detected in the replies and that Personal and Anonymous Twitter accounts belonging to right-wing and ideologically-driven users will send Tweets containing the most harassment to the female politicians.

Harassment or gendertrolling is defined as sexist or misogynistic remarks that target a person based on their gender or sexuality and have varying levels of severity [@wagner]. Severity of harassment includes:

1.  Positive

2.  Neutral

3.  Questioning authority

4.  Name-calling/Gender insults

5.  Vicious language

6.  Credible threats

7.  Hate speech

Type of account is defined as the dynamics of relationships between followers, followings, and lists and will be determined by analyzing the accounts' bio, profile image, and other characteristics [@singh; @uddin]. Types of accounts include:

1.  Personal

2.  Professional

3.  Bots

4.  Spammers

5.  Anonymous

6.  Suspended/deleted

My analysis reveals that 86% of all replies to Tweets about climate change and environmental policy that originated on the accounts of DPM Freeland, MP May, and MP Collins contain some form of harassment, ranging from Questioning authority to Hate speech. The remaining 14% of Tweets had either positive or neutral sentiments. Questioning the authority of female politicians, followed by Name-calling/Gender insults were the most common forms of harassment identified, accounting for over 80% of all Tweets. Harassing Tweets were most likely to be sent by Spammers or Anonymous accounts. My Bayesian hierarchical model suggests that there are no significant quantitative differences between the severity of harassment received by the three politicians, although qualitative differences, including word choices and tone were detected during the coding process. My [Discussion] section further explores these qualitative and quantitative differences, among other key findings.

In the remainder of this paper, I commence with the [Literature Review], followed by my [Theoretical Framework]. Next, I discuss my [Data and Methods]. Then, I highlight my [Results] and [Model], before providing further analysis and insights in the [Discussion] section. Finally, in the [Conclusion], I summarize my main findings.

# Literature Review

## Twitter & The Digital Public Sphere

The notion of having a public sphere for political deliberation is as old as Athenian democracy itself [@zizi2002]. In its simplest form, the public sphere is a place where "...society engages in critical public debate" [@habermas1989, p. 52] and meaning is "...generated, circulated, contested, and reconstructed" [@fraser1995, p. 287]. Although Jürgen Habermas wrote about the public sphere in the mid-twentieth century, eighteenth century bourgeois society served as the basis for his theory, overlooking how elites tried to influence and dominate the form political discourse took among other socio-economic classes [@mediatingmisogyny; @megarry2014]. Through Habermas' conceptualization, the public sphere intends to magnify the voices of the political elites (traditionally white men), while diminishing and even vilifying the voices of minorities -- traits which have been transposed into the digital public sphere [@mediatingmisogyny].

<!-- The past few decades have led to structural transformation and fragmentation of the idea of the public sphere, moving from having a singular, "official" public sphere to a multitude of smaller parallel ones, called "subaltern counterpublics" and networked publics mediated by technological affordances [@brunshighfield; @fraser1991; @boyd2010]. Technology reorganized the flow of information in society, distinguishing networked publics from subaltern counterpublics and the "official" public. Discourse traditionally happened in mediated spaces, but the rise of social media allows it to happen everywhere and is theoretically breaking down barriers of who has access to the walled garden of democratic discourse [@mediatingmisogyny; @trifiro]. Despite the potential formation of new publics online, the public which continues to deny the existence of climate change are largely white, male, and Christian and have free time (often dictated by patriarchal norms) to troll female politicians on Twitter whose actions as climate leaders do not fit traditional gender roles and conceptions of power [@Anshelm; @mccrightdunlap; @degeus; @mantilla2013]. Networked publics can be potent for democracy, undermining the authority of female politicians and risking the civility of democratic discourse. Consequently, women have and continue to be on the margins of the public sphere, both in physical spaces like the House of Commons and online, as underscored by an @ipu global survey which found that 82% of female politicians reported being subjected to psychological violence (including harassment, threats, and sexist comments). In Canada, specific examples of on-going marginalization can be seen through the lived realities of women in politics, with only one female Prime Minister, Rt. Hon. Kim Campbell in 1993, and in 2024, only 30% of MPs are female [@degeus; @hoc].  -->

The past few decades have led to the structural transformation and fragmentation of the public sphere, moving from having a singular, "official" public sphere to a multitude of parallel smaller ones, called "subaltern counterpublics" and networked publics mediated by technological affordances [@brunshighfield; @fraser1991; @boyd2010]. Technology reorganized the flow of information in society, distinguishing networked publics from subaltern counterpublics and the "official" public. Discourse traditionally happened in mediated spaces, but the rise of social media allows it to happen everywhere, theoretically breaking down barriers of who has access to the walled garden of democratic discourse [@mediatingmisogyny; @trifiro]. Despite the potential for the formation of new publics online, including issue publics driven by shared policy interests such as climate change, the leading voices in networked publics largely continue to be white, male, Christian, and have free time (often dictated by patriarchal norms) to actively contribute to discussions [@bruns2023; @mantilla2013; @degeus]. Networked publics use trolling and harassment to undermine the authority of female politicians whose actions do not fit traditional gender roles and conceptions of power [@degeus; @mantilla2015; @megarry2014]. Consequently, women have and continue to be on the margins of the public sphere, both in physical spaces like the House of Commons and online, as underscored by an @ipu global survey which found that 82% of female politicians reported being subjected to psychological violence (including harassment, threats, and sexist comments). In Canada, specific examples of on-going marginalization can be seen through the lived experiences of women in politics, with only one female Prime Minister to date (the Rt. Hon. Kim Campbell) and 30% of federal MPs being female [@degeus; @hoc].

The original mindset for the development of the internet in the second half of the twentieth century was one of utopianism and democratic renewal -- a new space for civil conversations [@zizi2002; @zizi2004]. However, early 2000s political communication theorists often overlooked the aims and agendas of the people who engineered these technologies [@zizi2004]. @megarrybook adds that the internet was seen as the "last frontier" for male domination, much like the classic image of the American Wild West. The behaviours and norms of the Wild West continue to play out through the actions of male tech CEOs, such as Elon Musk, and through the way platforms are governed. While often lacking in application, social media platforms including Twitter have slowly adopted rigorous content moderation and community safety policies [@overtime].

## Harassment of Women in Politics

Gender-based harassment and gendertrolling on Twitter is well-documented in the literature [@mediatingmisogyny; @carlson; @trifiro; @mantilla2013]. Previous research has started distinguishing traits of harassment based on a politician's status and visibility in politics and across traditional and social media. Blatant harassment is most likely to impact politicians of higher status and visibility, such as Cabinet Ministers [@rheault], while harassment of backbench MPs is often through more subtle, everyday microaggressions [@harmer]. Both  @collignon2020 and @erikson found that the intersection between a politician's age, gender, and political affiliation largely determines the type and frequency of harassment they face, leading to younger, female politicians more frequently receiving harassing messages than older politicians. Widespread and systematic harassment threatens meaningful political participation by women, the nature of policy debates in the House of Commons, and the future of democracy [@southern; @degeus]. While it is difficult to know precisely which combination of characteristics contribute to the intensity of harassment in the digital public sphere, harassment continues to be used as an equalizing force to silence the voices of women and maintain the status quo [@mantilla2015; @mccrightdunlap].

# Theoretical Framework

By employing the theory of deliberative democracy, this paper analyzes responses to Tweets sent by female politicians which explicitly discuss climate change and environmental policy to evaluate the extent at which they fulfill the characteristics of healthy democratic discourse. Often paired with their work on the public sphere, Jürgen Habermas and Richard Sennet are credited for publishing founding research on the theory of deliberative democracy [@kies2010]. Recently, communication and media studies scholars have reconceptualized the formation of the public sphere, evaluating the role of platforms with promised democratizing qualities, disinformation, and how these mediums impact the original notion of deliberative democracy [@bruns2023].

At its core, deliberative democracy "is a normative theory of democratic legitimacy based on the idea that those affected by a collective decision have the right, opportunity, and capacity to participate in consequential deliberation about the content of decisions" [@ercan, p. 23]. Democratic legitimacy is established by allowing the public to collectively participate in respectful and reasonable deliberation about consequential decisions, while recognizing that there are multiple viewpoints on every issue [@masullochen; @pmc2019; @mckaytenove]. @mckaytenove highlight that a new characteristic of deliberative democracy is the ability for those who participate in debate to do so in anonymous and pseudonymous ways, which both strengthen and undermine deliberation in different ways.

<!-- Diverging scholarly viewpoints exist when operationalizing and applying the theory of deliberative democracy. Some scholars view the theory in rigid terms, evaluating all characteristics and scenarios, such as political parties, systems, and institutions on a "yes" or "no" basis [@sokolon]. Sometimes, other scholars overlook or discount the role of social media and emerging technologies in creating networked publics which can drastically shape the quality and quantity of online democratic discourse. Moreover, other scholars view the theory of deliberative democracy on a scale - looking at the extent in which healthy democratic speech exists in specific contexts [@rossini]. Communication and media studies scholars are concerned about the nuances of discourse and the specific contexts in which it is situated and how algorithms and platform affordances are building and shaping these contexts [@bruns2023]. -->

Diverging scholarly viewpoints exist when operationalizing and applying the theory of deliberative democracy. Some scholars view the theory in rigid terms, evaluating all characteristics and scenarios, such as political parties, systems, and institutions on a "yes" or "no" basis [@sokolon]. However, as @rossini suggests, the theory of deliberative democracy can be viewed on a scale -- looking at the extent in which healthy democratic speech exists in specific contexts. In our increasingly digitized democracy, we cannot overlook or discount how algorithms and platform affordances are building the networks and contexts in which influential democratic deliberation takes place [@bruns2023].

In this paper, I adopt a "to what extent" perspective. This perspective aligns with the seven-point scale I developed to measure the severity of harassment on the basis that democratic discourse is nuanced and relies both on traditional democratic theory and contemporary approaches to media studies [@bruns2023]. This approach recognizes that shades of civil and uncivil speech simultaneously exist in the digital public sphere. Furthermore, I assume the perspective that to some degree, healthy disagreement is accepted and needed (aligning with @rossini), but not to the extent of female politicians self-censoring out of fear for their physical and psychological safety. Results from my data analysis and model will be evaluated, using the aforementioned definition and characteristics of deliberative democracy, to see the extent in which the discourse among the Tweets in my dataset can be considered healthy for Canadian democracy.

# Data and Methods

## Data Collection

All Twitter data was collected throughout the month of October 2023 using the statistical programming software R [@r] and functions from `voson.tcn` [@gertzel2021] and the `tidyverse` [@rTidyverse]. Paid access to Twitter's Basic v2 Application Programming Interface (API) endpoint was obtained before using the advanced search feature to determine which Tweets I wanted to download via the API. My sample includes any original Tweets written in English (no quote or Retweets) that originated on the accounts of DPM Freeland (\@cafreeland), MP May (\@elizabethmay), and MP Collins (\@laurel_bc) that were posted between September 1, 2022, and October 31, 2023. Tweets also had to the contain the word "climate,” "environment,” and/or "environmental" (as part of the text of the Tweet or as a hashtag). For threaded Tweets sent by the politicians, the first Tweet of the thread had to contain at least one of the key words and the overall focus of the thread had to be on climate change and/or environmental policy. For Tweet threads that mentioned one of the key words in later Tweets and in passing, these Tweets and replies were omitted due to their lack of relevance. Key words were also checked for applicability, given the use of words such as "climate" and "environment" to reference geopolitics and economic situations and not actual climate or environmental policy. Within the parameters of the sample, DPM Freeland's Tweets were from October 2022 to October 2023 and had either the key word "climate" or "environment". MP May's Tweets were from September 2022 to October 2023 and included the words "climate," "environment," and "environmental". Lastly, MP Collins' Tweets were from October 2022 to October 2023 and included the words "climate," "environment," and "environmental."

I ultimately collected 11 original Tweets from DPM Freeland, 32 original Tweets from MP May, and 25 original Tweets from MP Collins. Between all the original Tweets and replies, there were 2,424 Tweets for DPM Freeland, 1,094 Tweets for MP May, and 711 Tweets for MP Collins for a total of 4,229, before cleaning the datasets. The distribution of the number of original Tweets and associated replies was anticipated, given @rheault finding that status and visibility impact the quantity of harassment faced by Canadian politicians.

## Data Cleaning

### Raw Data

The raw datasets underwent multiple cleaning procedures and tests before being ready to manually code. Cleaning refers to the process of preparing a raw dataset for further analysis, ensuring basic aspects like each Tweet and corresponding account metadata has its own column, row, and cell, before moving onto project-specific preparations [@tellingstories]. Cleaning serves as a useful process for identifying anomalies in the dataset, such as mis-matched Tweets and account metadata. The `voson.tcn` package provided several columns of Twitter metadata that was not relevant to the objectives of this paper, so I eliminated those and focused on columns such as the text of the Tweet, the user's location, bio, profile picture, and whether they paid to be verified with a blue checkmark through Twitter's subscription program. All raw and coded data cleaning was done using R [@r], utilizing functions from the `tidyverse` [@rTidyverse] and `janitor` [@rJanitor]. The original Tweets and replies sent by the female politicians in response to their own thread (known as a threaded Tweet) were omitted during the cleaning process. The few replies sent in languages other than English, including French, Ukrainian, German, and Arabic were removed. Testing of the combined and cleaned datasets was conducted using `validate` [@validate] before being manually coded. The final number of Tweets left following these cleaning procedures are displayed in @tbl-breakdown, which highlights that DPM Freeland is overrepresented in my sample.

```{r}
#| message: false
#| eval: true
#| echo: false
#| label: tbl-breakdown
#| tbl-cap: Number of replies and their overall percentage of the sample by female politician following the data cleaning process

finalized_cleaned_tweets |>
  group_by(name_of_politician) |>
  count() |>
  ungroup() |>
  mutate(pct = paste0(round((n / sum(n)) * 100), "%")) |>
  arrange(match(name_of_politician, c('Chrystia Freeland', 'Elizabeth May', 'Laurel Collins'))) |>
  kable(
    col.names = c("Name of Politician", "Number of Replies", "Percentage"),
    booktabs = TRUE,
  )

```

### Coded Data

After manually coding the 4,139 Tweets using my Google Form and Codebook (see [Appendix]), I proceeded to the second round of cleaning the Tweets using R [@r]. I eliminated columns of data which were useful for determining the type of account but not relevant for the next steps of my analysis. For my severity of harassment data, I updated value 1 to "Positive," 2 to "Neutral," 3 to "Questioning authority," 4 to "Name-calling/Gender insults," 5 to "Vicious language," 6 to "Credible threats," and 7 to "Hate speech" based on my Codebook. Furthermore, for my type of account data, I changed value 1 to "Personal," 2 to "Professional," 3 to "Bots," 4 to "Spammers," 5 to "Anonymous," and 6 to "Suspended/deleted" based on my Codebook. I tested the cleaned data using `validate` [@validate], primarily validating variable types and ensuring the number of rows in the dataset matches the number of Tweets I coded. I then analyzed and visualized my data in R [@r], using functions from `knitr` [@rknitr], `kableExtra` [@rKableExtra], `Formattable` [@rFormattable], and `ggplot2` [@rGgplot2].

## Data Coding

### Codebook

I developed a comprehensive codebook building on previous research and a sample of Tweets (see [Appendix]). Severity of harassment is coded on a seven-point scale, with the seven categories being: Positive, Neutral, Questioning authority, Name-calling/Gender insults, Vicious language, Credible threats, and Hate speech. There is agreement among scholars from fields such as communication and media studies, women and gender studies, and political science that there are no universal definition or ways of measuring and characterizing severity of harassment, incivility, and hate speech [@mantilla2015; @tenove; @krook2020]. Through this study, I develop and test a new quantitative seven-point scale which contributes to on-going research by emphasizing everyday forms of harassment, such as microaggressions and questioning the authority of female politicians. These more everyday forms of harassment are often missed during binary coding conducted by large language models (LLMs). My seven-point scale also combines the nuance from previous qualitative projects which employ content analysis and interviews, while recognizing the benefits of more statistical and quantitative approaches offered by computational political communication researchers.

## Data Limitations

Twitter, the platform's affordances, and the types of accounts and content circulating is ever-changing. A major limitation of using Twitter data for any research is the inability to determine a representative sample of voting-age Canadians and draw generalizable results about public opinion on any given issue [@bermingham]. Selection bias exists because Twitter tends to only represent the views of people who are "...more partisan, polarized, and uncivil" and motivated to be active users [@mcgregor, p. 237]. We are also limited by the information users choose to publicly display on their profiles, such as their location, so it is not always possible to confirm if an individual is Canadian or other identifying demographic information [@holmberg]. Due to the global and open nature of social media platforms, some of the Tweets captured are from users who claim to be in the United States, the United Kingdom, and Australia, therefore limiting our ability to solely see the behaviours of Canadian users.

Moreover, Twitter data is collected as a snapshot in time, often reducing users to a single interaction on the platform, meaning we cannot see their full range of political expressions and frequency of certain behaviours, leading to potential measurement bias. Consequently, with context collapse which happens when an individual users' Tweets are taken out of the context and imagined audience in which they were intended for, users' true political beliefs, views on climate change, and perspectives on the qualifications of women in politics may be misrepresented [@contextcollapse]. Some users may also show up more than once in the dataset if they are prolific Twitter users, leading to overrepresentation of their views and type of account. With these identified limitations in mind, results should be considered in the context of this study and generalizations can only be reflective of the users in the dataset and not the wider Canadian public.

There are several restrictions placed on the storage and sharing of data collected via Twitter's API, limiting the reproducibility of this research project [@tellingstories; @Twittermedia]. Datasets, even if personally identifying information such as usernames and locations have been removed, cannot be uploaded to open source platforms like GitHub. While advancing our understanding of the harassment faced online by Canadian female politicians, I am ensuring that proper steps are taken to not further victimize female politicians through ethical data storage and analysis [@krook2020].

# Results

## Severity of Harassment

```{r}
#| message: false
#| eval: true
#| echo: false
#| label: tbl-severity
#| tbl-cap: Breakdown of Severity of Harassment on the seven-point scale detected in Tweets to all three politicians

finalized_cleaned_tweets |>
  group_by(severity_of_harassment) |>
  count() |>
  ungroup() |>
  mutate(pct = paste0(round((n / sum(n)) * 100), "%")) |>
  arrange(match(severity_of_harassment, c('Positive', 'Neutral', 'Questioning Authority', 'Name-calling/Gender insults', 'Vicious language', 'Credible threats', 'Hate speech'))) |>
  kable(
    col.names = c("Severity of Harassment", "Number of Replies", "Percentage"),
    booktabs = TRUE,
  ) 
```

Among the 4,139 Tweets from the three female politicians, 2,284 (55%) were identified as Questioning authority, 1,060 (26%) as Name calling/Gender insults, and 542 (13%) as Neutral (see @tbl-severity). 144 (3%) contained Vicious language, while Positive, Credible threats, and Hate speech all respectively accounted for 1% of the Tweets detected. For all three politicians, the most frequently selected categories are Questioning authority, followed by Name-calling/Gender insults, and Neutral.

## Type of Account

```{r}
#| message: false
#| eval: true
#| echo: false
#| label: tbl-accounts
#| tbl-cap: Breakdown of Type of Accounts detected in replies to all three female politicians

finalized_cleaned_tweets |>
  group_by(type_of_account) |>
  count() |>
  ungroup() |>
  mutate(pct = paste0(round((n / sum(n)) * 100), "%")) |>
  arrange(match(type_of_account, c('Personal', 'Professional', 'Bots', 'Spammers', 'Anonymous', 'Suspended/deleted'))) |>
  kable(
    col.names = c("Type of Account", "Number of Accounts", "Percentage"),
    booktabs = TRUE,
  )

```

@tbl-accounts summarizes the distribution of types of accounts identified. Spammers accounted for 1,071 (41%) of all accounts, followed by 1,515 (37%) Anonymous accounts, and 802 (19%) Personal accounts. Small numbers of accounts categorized as Suspended/deleted (2%), Professional (1%), and Bots (0%) were detected, which will be further examined in [Discussion] and [Limitations]. While some users sent multiple replies to either one, two, or all of the female politicians, over 75% of users only appeared once in the dataset, aligning with previous results from @theocharis and @ward2020.

<!-- length(unique(finalized_cleaned_tweets$username)) While some users sent multiple replies to either one, two, or all of the female politicians, over 75% of users only appeared once in the dataset. My type of account results are consistent with the findings of @theocharis and @ward2020, who reveal that "... uncivil behavior seems to be common among many frustrated citizens who take to Twitter to angrily criticize and insult politicians" [@theocharis, p. 9]. -->

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-accounts_all
#| fig-cap: Type of Accounts behind the Tweets received, broken down by politician

finalized_cleaned_tweets |>
  mutate(type_of_account = fct_relevel(type_of_account, "Personal", "Professional", "Bots", "Spammers", "Anonymous", "Suspended/deleted")) |>
  ggplot(mapping = aes(x = type_of_account, fill = name_of_politician)) +
  geom_bar(position = "dodge2", aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 8)) +
  theme(axis.title.x = element_text(size = 9)) + 
  theme(axis.title.y.left = element_text(size = 9)) + 
  labs(x = "Type of Account", y = "Percentage of Accounts", fill = "Politician") +
  theme(legend.position = "bottom") +
  theme(legend.text = element_text(size = 6)) +
  theme(legend.title = element_text(size = 9)) +
  scale_fill_viridis_d()

```

## Chrystia Freeland

For DPM Freeland, 1,189 (50%) of her Tweets were categorized as Questioning authority, followed by Name-calling/Gender insults with 678 (28%), and 356 (15%) Neutral Tweets (see @tbl-chrystia_severity). 99 (4%) of her Tweets contained Vicious language, with the remaining categories of Positive, Credible threats, and Hate speech each accounting for 1% of the total Tweets. The fewest number of Tweets in DPM Freeland's sample were categorized as Positive, with Hate speech being more prominent, which illustrates the increasingly toxic nature of discourse directed at DPM Freeland.

```{r}
#| message: false
#| eval: true
#| echo: false
#| label: tbl-chrystia_severity
#| tbl-cap: Breakdown of the Severity of Harassment on the seven-point scale detected among DPM Freeland's Tweets

finalized_cleaned_tweets |>
  filter(name_of_politician == "Chrystia Freeland") |>
  group_by(severity_of_harassment) |>
  count() |>
  ungroup() |>
  mutate(pct = paste0(round((n / sum(n)) * 100), "%")) |>
  arrange(match(severity_of_harassment,  c('Positive', 'Neutral', 'Questioning Authority', 'Name-calling/Gender insults', 'Vicious language', 'Credible threats', 'Hate speech'))) |>
  kable(
    col.names = c("Severity of Harassment", "Number of Accounts", "Percentage"),
    booktabs = TRUE,
  ) 
```

As illustrated by @tbl-chrystia_account, Spammers and Anonymous accounts made up 80% of all identified accounts, followed by 418 (17%) Personal accounts. Very small numbers of Professional, Bots, and Suspended/deleted accounts were detected.

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-chrystia_account
#| tbl-cap: Breakdown of the Types of Accounts detected among DPM Freeland's Tweets

finalized_cleaned_tweets |>
  filter(name_of_politician == "Chrystia Freeland") |>
  group_by(type_of_account) |>
  count() |>
  ungroup() |>
  mutate(pct = paste0(round((n / sum(n)) * 100), "%")) |>
  arrange(match(type_of_account, c('Personal', 'Professional', 'Bots', 'Spammers', 'Anonymous', 'Suspended/deleted'))) |>
  kable(
    col.names = c("Type of Account", "Number of Accounts", "Percentage"),
    booktabs = TRUE,
  )

```

For DPM Freeland, the relationship between severity of harassment and type of account can be seen in @fig-freeland_relationship. Positive and Neutral Tweets were most frequently sent by Personal accounts, while Tweets Questioning authority and Name-calling/Gender insult most frequently came from Anonymous accounts, closely followed by Spammers. Anonymous accounts, closely followed by Spammers, were responsible for sending the most Tweets containing Vicious language, while Credible threats and Hate speech were most often sent by Spammers.

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-freeland_relationship
#| fig-cap: Relationship between Severity of Harassment and Types of Accounts detected among DPM Freeland's Tweets

finalized_cleaned_tweets |>
  filter(name_of_politician == "Chrystia Freeland") |>
  mutate(severity_of_harassment = fct_relevel(severity_of_harassment, "Positive", "Neutral", "Questioning Authority", "Name-calling/Gender insults", "Vicious language", "Credible threats", "Hate speech")) |>
  mutate(type_of_account = fct_relevel(type_of_account, "Personal", "Professional", "Bots", "Spammers", "Anonymous", "Suspended/deleted")) |>
  ggplot(mapping = aes(x = severity_of_harassment, fill = type_of_account)) +
  geom_bar(position = "dodge2", aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 8)) +
  theme(axis.title.x = element_text(size = 9)) + 
  theme(axis.title.y.left = element_text(size = 9)) + 
  labs(x = "Severity of Harassment", y = "Percentage of Tweets", fill = "Type of Account") +
  theme(legend.position = "bottom") +
  theme(legend.text = element_text(size = 6)) +
  theme(legend.title = element_text(size = 9)) +
   scale_fill_brewer(palette = "Set1")

```

## Elizabeth May

Among the sample of MP May's Tweets, 583 (55%) were categorized as Questioning authority, 295 (28%) as Name-calling/Gender insults, and 133 (13%) as Neutral (details in @tbl-liz_severity). 12 (1%) of the Tweets in MP May's sample were Positive, with 1 (0%) Tweet belonging to both the Credible threats and Hate speech categories.

```{r}
#| message: false
#| eval: true
#| echo: false
#| label: tbl-liz_severity
#| tbl-cap: Breakdown of the Severity of Harassment on the seven-point scale detected among MP May's Tweets

finalized_cleaned_tweets |>
  filter(name_of_politician == "Elizabeth May") |>
  group_by(severity_of_harassment) |>
  count() |>
  ungroup() |>
  mutate(pct = paste0(round((n / sum(n)) * 100), "%")) |>
  arrange(match(severity_of_harassment,  c('Positive', 'Neutral', 'Questioning Authority', 'Name-calling/Gender insults', 'Vicious language', 'Credible threats', 'Hate speech'))) |>
  kable(
    col.names = c("Severity of Harassment", "Number of Accounts", "Percentage"),
    booktabs = TRUE,
  ) 
```

@tbl-liz_account emphasizes that 502 (47%) of the accounts in MP May's sample belong to Spammers, followed by 323 (31%) Anonymous accounts, and 198 (19%) Personal accounts. Moreover, 21 (2%) of accounts in MP May's sample are Suspended/deleted, 12 (1%) Professional, and 2 (0%) Bots.

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-liz_account
#| tbl-cap: Breakdown of the Types of Accounts detected among MP May's Tweets

finalized_cleaned_tweets |>
  filter(name_of_politician == "Elizabeth May") |>
  group_by(type_of_account) |>
  count() |>
  ungroup() |>
  mutate(pct = paste0(round((n / sum(n)) * 100), "%")) |>
  arrange(match(type_of_account, c('Personal', 'Professional', 'Bots', 'Spammers', 'Anonymous', 'Suspended/deleted'))) |>
  kable(
    col.names = c("Type of Account", "Number of Accounts", "Percentage"),
    booktabs = TRUE,
  )

```

The relationship between severity of harassment and type of account in Tweets sent to MP May can be seen in @fig-may_relationship. Positive and Neutral Tweets most frequently were sent by Personal accounts, while Tweets Questioning authority and Name-calling/Gender insult most frequently came from Spammers. Anonymous accounts were responsible for sending the most Tweets containing Vicious language, while Credible threats were only sent by Anonymous accounts and Hate speech was only sent by Spammers.

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-may_relationship
#| fig-cap: Relationship between Severity of Harassment and Types of Accounts detected among MP May's Tweets

finalized_cleaned_tweets |>
  filter(name_of_politician == "Elizabeth May") |>
  mutate(severity_of_harassment = fct_relevel(severity_of_harassment, "Positive", "Neutral", "Questioning Authority", "Name-calling/Gender insults", "Vicious language", "Credible threats", "Hate speech")) |>
  mutate(type_of_account = fct_relevel(type_of_account, "Personal", "Professional", "Bots", "Spammers", "Anonymous", "Suspended/deleted")) |>
  ggplot(mapping = aes(x = severity_of_harassment, fill = type_of_account)) +
  geom_bar(position = "dodge2", aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 8)) +
  theme(axis.title.x = element_text(size = 9)) + 
  theme(axis.title.y.left = element_text(size = 9)) + 
  labs(x = "Severity of Harassment", y = "Percentage of Tweets", fill = "Type of Account") +
  theme(legend.position = "bottom") +
  theme(legend.text = element_text(size = 6)) +
  theme(legend.title = element_text(size = 9)) +
   scale_fill_brewer(palette = "Set1")

```

## Laurel Collins

Of the Tweets in MP Collins' sample, 512 (75%) were categorized as Questioning authority, 87 (13%) as Name-calling/Gender insults, and 53 (8%) as Neutral. As shown in @tbl-laurel_severity, the remaining Tweets were categorized as Positive (13 or 2%), Vicious language (12 or 2%), Credible threats and Hate speech (2 Tweets per category or 0%).

```{r}
#| message: false
#| eval: true
#| echo: false
#| label: tbl-laurel_severity
#| tbl-cap: Breakdown of the Severity of Harassment on the seven-point scale detected among MP Collins' Tweets

finalized_cleaned_tweets |>
  filter(name_of_politician == "Laurel Collins") |>
  group_by(severity_of_harassment) |>
  count() |>
  ungroup() |>
  mutate(pct = paste0(round((n / sum(n)) * 100), "%")) |>
  arrange(match(severity_of_harassment,  c('Positive', 'Neutral', 'Questioning Authority', 'Name-calling/Gender insults', 'Vicious language', 'Credible threats', 'Hate speech'))) |>
  kable(
    col.names = c("Severity of Harassment", "Number of Accounts", "Percentage"),
    booktabs = TRUE,
  ) 
```

For MP Collins, 68% of the accounts were categorized as both Spammers and Anonymous, followed by Personal (186 or 27%). As seen in @tbl-laurel_account, the remaining accounts were categorized as Professional (19 or 3%), Suspended/deleted (10 or 1%), and Bots (1 or 0%).

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-laurel_account
#| tbl-cap: Breakdown of the Types of Accounts detected among MP Collins' Tweets

finalized_cleaned_tweets |>
  filter(name_of_politician == "Laurel Collins") |>
  group_by(type_of_account) |>
  count() |>
  ungroup() |>
  mutate(pct = paste0(round((n / sum(n)) * 100), "%")) |>
  arrange(match(type_of_account, c('Personal', 'Professional', 'Bots', 'Spammers', 'Anonymous', 'Suspended/deleted'))) |>
  kable(
    col.names = c("Type of Account", "Number of Accounts", "Percentage"),
    booktabs = TRUE,
  )

```

@fig-collins_relationship emphasizes the relationship between severity of harassment and type of account. Positive, Neutral, and Credible threats Tweets were most frequently sent by Personal accounts, while Tweets Questioning authority and Name-calling/gender insults most frequently came from Spammers, closely followed by Anonymous accounts. Additionally, Anonymous accounts were responsible for sending the most Tweets containing Vicious language, while Hate speech was equally sent by Spammers and Anonymous accounts.

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-collins_relationship
#| fig-cap: Relationship between Severity of Harassment and Types of Accounts detected among MP Collins' Tweets

finalized_cleaned_tweets |>
  filter(name_of_politician == "Laurel Collins") |>
  mutate(severity_of_harassment = fct_relevel(severity_of_harassment, "Positive", "Neutral", "Questioning Authority", "Name-calling/Gender insults", "Vicious language", "Credible threats", "Hate speech")) |>
  mutate(type_of_account = fct_relevel(type_of_account, "Personal", "Professional", "Bots", "Spammers", "Anonymous", "Suspended/deleted")) |>
  ggplot(mapping = aes(x = severity_of_harassment, fill = type_of_account)) +
  geom_bar(position = "dodge2", aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 8)) +
  theme(axis.title.x = element_text(size = 9)) + 
  theme(axis.title.y.left = element_text(size = 9)) + 
  labs(x = "Severity of Harassment", y = "Percentage of Tweets", fill = "Type of Account") +
  theme(legend.position = "bottom") +
  theme(legend.text = element_text(size = 6)) +
  theme(legend.title = element_text(size = 9)) +
   scale_fill_brewer(palette = "Set1")

```

# Model

I am interested in seeing why some Twitter users are more predisposed than others to send harassing Tweets to Canadian female politicians. In particular, I want to further investigate the combination of the type of account a user has, whether they are verified, and which politician they are replying to in order to predict if they are more likely to send a harassing Tweet. Historically, accounts with the blue checkmark/tick were regarded as credible individuals and/or organizations, sharing legitimate information [@unverified]. However, since Musk introduced changes to Twitter's verification policy in April 2023, the @CCDHreport found that 99% of online hate was spread by malicious users who paid to be verified, allowing for circumvention of content moderation rules. Bayesian hierarchical modeling using the statistical programming language R [@r], employing `rstanarm` [@rstanarm], `marginaleffects` [@marginal], and `modelsummary` [@modelsummary] can help predict and further investigate this relationship. The model was fit in a Bayesian framework using `rstanarm` [@rstanarm]. For the priors, I followed the standard weakly informed prior distributions by using the normal definition with mean 0 and standard deviation 2.5 as used in the `rstanarm` package.

$$
\begin{aligned}
y_i|\pi_i & \sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) & = \beta_0 + \alpha_{a[i]}^{\mbox{account}} + \alpha_{p[i]}^{\mbox{politician}} + \alpha_{v[i]}^{\mbox{verified}} \\
\alpha_0 & \sim \mbox{Normal}(0, 2.5)\\
\alpha_{a}^{\mbox{acc}} & \sim \mbox{Normal}\left(0, \sigma^2_{\mbox{acc}}\right)\mbox{ for }a = 1, 2, \dots, A\\
\alpha_{p}^{\mbox{pol}} & \sim \mbox{Normal}\left(0, \sigma^2_{\mbox{pol}}\right)\mbox{ for }p = 1, 2, 3, P\\
\alpha_{v}^{\mbox{ver}} & \sim \mbox{Normal}\left(0, \sigma^2_{\mbox{ver}}\right)\mbox{ for }v = 0, 1, V\\
\sigma_{\mbox{acc}} & \sim \mbox{Exponential}(1)\\
\sigma_{\mbox{pol}} & \sim \mbox{Exponential}(1) \\
\sigma_{\mbox{ver}} & \sim \mbox{Exponential}(1)
\end{aligned}
$$ Where $y_i$ is whether a Tweet contained harassment, $\pi_i = \mbox{Pr}(y_i=1)$, and $\alpha^{\mbox{account}}$, $\alpha^{\mbox{politician}}$, and $\alpha^{\mbox{verified}}$ and are the effect of the type of account a user has, which politician they are replying to, and whether their account is verified. The $a[i]$, $p[i]$, and $v[i]$ refer to which type of account, which politician, and whether a user is verified. $A$, $P$, and $V$ are the total number of types of accounts, politicians, and verification options, respectively. The binary response variable, called `harassment_binary`, has a value of 0 if a Tweet does not contain harassment and a value of 1 if it contains harassment. The Positive and Neutral categories on my seven-point scale make up the value of 0 and all remaining categories (Questioning authority through Hate speech) make up the value of 1.

```{r}
#| echo: false
#| eval: true
#| label: tbl-modsummary
#| tbl-cap: Predicting whether a Tweet contains harassment or not, on the basis of the type of account behind the Tweet, which politician the Tweet was in response to, and whether a user is verified.
#| message: false
#| warning: false

harassment_model <- readRDS(here::here("Outputs/Model/harassment_model.rds"))

modelsummary(list(harassment_model))

```
@tbl-modsummary presents the estimates generated by the model. For ease of analysis, @tbl-marginal displays the estimates as predictions in a table and @fig-plotted shows the predictions graphed.

```{r}
#| echo: false
#| eval: true
#| label: tbl-marginal
#| tbl-cap: Predicting whether a Tweet contains harassment or not, on the basis of the type of account behind the Tweet, which politician the Tweet was in response to, and whether a user is verified.
#| message: false
#| warning: false

harassment_model <- readRDS(here::here("Outputs/Model/harassment_model.rds"))

slopes(harassment_model, newdata = "median") |>
  select(term, contrast, estimate) |>
  kable(
    col.names = c("Term", "Contrast", "Estimate"),
    digits = 2, booktabs = TRUE
  )

```

@tbl-marginal predicts whether a user is likely to send replies that contain harassment as a function of their type of account, whether their account is verified, and which female politician they are replying to. When compared to DPM Freeland, Tweets sent to MP May are an estimated 2% more likely to not contain harassment, while MP Collins is an estimated 6% more likely to receive Tweets that do not contain harassment in comparison to DPM Freeland. For type of account, when personal accounts are compared to professional accounts, professional accounts are an estimated 13% less likely to send Tweets that do not contain harassment. Bots, when compared to personal accounts, are an estimated 8% more likely to send Tweets that do not contain harassment, while Spammers are an estimated 11% and Anonymous accounts an an estimated 12% more likely to send Tweets which do not contain harassment. Suspended/deleted accounts are an estimated 3% more likely send Tweets that do not contain harassment in comparison to personal accounts. The model is unable to find a quantitative difference in whether users who are verified or not verified are more likely to send harassing Tweets. The results from the model suggest that despite differences in status and political affiliation across the three politicians, they are almost equally impacted by harassment on Twitter. Moreover, all types of accounts are predisposed to sending harassing Tweets, especially Professional accounts, which I did not hypothesize, but will be explained in my [Discussion] section.

```{r}
#| echo: false
#| eval: true
#| label: fig-plotted
#| fig-cap: Predicting whether a Tweet contains harassment or not, on the basis of the type of account behind the Tweet, which politician the Tweet was in response to, and whether a user is verified.
#| message: false
#| warning: false

harassment_model <- readRDS(here::here("Outputs/Model/harassment_model.rds"))

harassment_model_predictions <-
  predictions(harassment_model)

harassment_model_predictions |>
  ggplot(aes(x = harassment_binary, y = estimate, color = name_of_politician)) +
  geom_jitter(width = 0.2, height = 0.0, alpha = 0.3) +
  labs(
    x = "Harassment",
    y = "Estimated probability that a Tweet contains harassment",
    color = "Name of Politician"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 8)) + 
  theme(axis.text.y = element_text(size = 8)) + 
  theme(axis.title.y = element_text(size = 8)) +
  theme(legend.position = "bottom") +
  theme(legend.text = element_text(size = 6)) +
  theme(legend.title = element_text(size = 9))

```

# Discussion

## Severity of Harassment

Based on my hypothesis, I expected that DPM Freeland, followed by MP May, then MP Collins would receive the most severe Tweets, however, MP Collins had more identified instances of Credible threats and Hate speech than MP May (for Hate speech, DPM Freeland had 29 instances, MP Collins had 2, and MP May had 1). I expected that everything of DPM Freeland's would be more severe -- with more identified instances of Hate speech and more Credible threats. She still receives considerable amounts of harassment though and being called a "Nazi" constantly was more severe than some of the other names MP May and MP Collins were called. This could be a weakness of my seven-point scale that being called "useless" and a "Nazi" fell under the same category of Name-calling/Gender insults. Qualitative differences such as these could lead me to further refine my quantitative scale.

55% of Tweets fell under the Questioning authority category, which was ultimately higher than hypothesized (see @tbl-severity). As seen in @tbl-qa-example, Tweets which are categorized as Questioning authority differ from information-seeking questions because users intend to question the abilities of female politicians based on their political affiliation, gender, age, physical appearance, and corresponding assumed qualifications. Although being questioned and tested may not seem like a specifically severe form of harassment, constant microaggressions and undermining comments from the public have been shown to lead female politicians to self-censor and retract from public deliberation, even going as far as deciding not to seek re-election [@harmer]. Self-censorship and retraction from public life is the opposite of what is needed for gender equality and climate action in politics [@mediatingmisogyny].

| Tweet                                                                  |
|------------------------------------------------------------------------|
| \@cafreeland \@G7 Good topics. Maybe add energy security. And be sure to take notes, because you haven't made progress on any of them. That said, you have made and continue to make, all Canadians poorer. |

: Sample of a Tweet **Questioning authority** sent to DPM Freeland. {#tbl-qa-example}

## Type of Account

For the types of accounts, there were more Spammers and Anonymous accounts than I hypothesized, but these results align with previous research and our understanding of the increasingly toxic nature of Twitter [@phillips; @wagner; @theocharis]. The high percentage of Anonymous accounts (37%) reinforces @mckaytenove's findings that anonymous (and often harassing) political speech is increasingly common in our contemporary era of deliberative democracy. Given recent changes to Twitter's affordances, Anonymous accounts continue to exist because people are not pleased with the new direction of the platform and do not wish to actively engage, but still wish to have an account.

The high number of Spammers (41%) is consistent with the "Wild West" attitude conceptualized by @megarrybook. Under previous ownership, many of these accounts would likely be suspended because of enforcement of content moderation rules. The low number of Suspended/deleted accounts was anticipated, because no one is held accountable for their actions anymore. The few deleted accounts were likely people who intentionally wanted to leave the platform. Of those people who are suspended, there are identified instances of temporary suspension (@Twittermedia) or permanent suspension, which users circumvented by making a new account. Users who made new accounts often indicated this in their bio through phrases like "Back again, hunting libs" or "3rd time? \@TXIndep1836 & \@TXIndepndnt1836 SILENCED!"

For all three politicians, Positive and Neutral Tweets were most likely to be sent by Personal users, while nearly all other categories of Tweets (Questioning authority through to Hate speech) were most likely to be sent by Anonymous and Spammer accounts. These findings are consistent with the work of @mckaytenove, @theocharis, and @ward2020, who suggest that anonymous and pseudonymous political uses of social media are increasing, but average citizens continue to use social media to weigh in on consequential policy issues and seek information from their federal representatives (instead of engaging through traditional means like email correspondence and town halls).

Although only 1% of accounts were identified as being Professional, who they belong to and their corresponding severity of harassment is notable. Of the replies which were sent by Professional accounts, 64% contained some form of harassment, most often Questioning authority or Name-calling/gender insults. A number of prominent Conservative MPs, including Federal Conservative Leader Pierre Polievre and MPs Stephanie Kusie and Larry Brock responded to Tweets originating on DPM Freeland's account. The estimate the model produced suggesting that Professional accounts are 13% less likely to send a Tweet that does not contain harassment is noteworthy because it illustrates how Conservative politicians are pandering to their base by engaging in aggressive, confrontational behaviour in the House of Commons and mimicking that behaviour online by sending harassing Tweets [@delacourt]. Tweets sent by Conservative MPs were coded as either Questioning authority or Name-calling/Gender insults, which suggests a level of disregard for Parliament as an institution, the authority of female politicians who work on climate and environmental policy, and deliberative democratic speech.

While coding type of accounts, I noticed a number of accounts had at least one red apple emoji and/or sometimes a green apple emoji in their bio or display name. Although there is no academic literature yet to explain this trend, I believe that Conservative supporters added this emoji to their profile as a sign of support for Leader Pierre Polievre, following his October 2023 viral video "chomping down" on an apple while scolding a journalist [@apples]. At the time of data collection, 90 unique users added apple emojis to their display name and/or bio, but that number is likely higher with the trend's increasing popularity. @tbl-apples provides an example. This subtle show of support for the Conservative Party is augmented by direct support for Conservative and right wing political movements in Canada and the United States by the use of words and phrases in user bios such as "#TrudeauMustGo," "#Pierre4PM," "#Trump2024," "MAGA," "CPC," "Conservative," and "PPC". 288 unique users in my dataset explicitly identified themselves as having right-wing and ideological views, which supports my hypothesis.

```{r}
#| echo: false
#| eval: true
#| label: tbl-apples
#| tbl-cap: Example of how Twitter users chose to show their support for the Conservative Party and their Leader through the use of the red apple emoji in their display name
#| message: false
#| warning: false

combined_apple_data |>
  select(name) |>
  slice_tail(n = 5) |>
  kable(
    col.names = c("Name"),
    booktabs = TRUE,
  )
```

## Chrystia Freeland

DPM Freeland's results for severity of harassment and type of account are largely consistent with my expectations and previous research into the harassment faced by eminent female politicians [@rheault]. The use of memes, to undermine and harass DPM Freeland prominently features in her sample of Tweets. The term, meme, was first used by evolutionary biologist Richard Dawkins in 1976 and is "... derived from the Greek *mimema*, meaning 'something imitated'; the current usage refers to an idea or bit of content that spreads widely through cyberspace" [@bauman, pp. 87-88]. The memes in DPM Freeland's sample are often unflattering photographs of her, presenting anti-feminist narratives, and intending to undermine her based on her physical appearance [@ging]. There was no evidence of deepfakes or highly sophisticated manipulated audiovisual content detected in DPM Freeland's sample [@appel]. Moreover, historical pictures from Nazi Germany in the 1930s/1940s were memed to include the faces of DPM Freeland and sometimes Prime Minister Rt. Hon. Justin Trudeau and NDP Leader Jagmeet Singh, aligning with research conducted by @frosh which reveals that the revival of historic photographs in the form of memes bolsters public discussion and draws symbolic connections between the past and present. The memes sent in response to Tweets by DPM Freeland are similar to anti-suffragette posters circulating in the early twentieth century which intended to undermine women campaigning for the right to vote and discourage the voices of women in the public sphere [@ging; @mckaytenove]. Memes and photographs, including the one below, are subjected to Twitter’s content moderation rules, as hate speech can be expressed through symbols and images, yet continue to freely circulate on the platform [@Twittermedia; @carlson].

![Example of a reply to a Tweet sent by DPM Freeland which revives historical photographs through memes and contains **Hate Speech**](hate_speech_example.png){width="400"}

Although there were only 29 identified instances of Hate speech in DPM Freeland's sample (see @tbl-chrystia_severity), qualitative signs of far-right activity and hateful behaviour appeared throughout her sample. Users belonging to fringe minorities will often assign ironic humor and hateful meanings to seemingly normal words and objects, such as the Pepe the Frog character which originated on 4chan, allowing later denial of their political views if questioned [@HolocaustEdu]. A number of users made reference to Pepe in either their username, bio, profile picture, or in their individual replies to Tweets that originated on DPM Freeland's account. Furthermore, at least one user in DPM Freeland's sample also stated their involvement in the far right online men’s rights movement called "men going their own way" (MGOW) [@maletears]. These preliminary observations of qualitative far right behaviour are concerning for the future of democracy and the active participation of women in politics.

## Elizabeth May
The results for severity of harassment and type of accounts detected in MP May's sample of Tweets are largely consistent with my hypothesis, although there were slightly fewer Positive and Neutral Tweets than anticipated. 55% of Tweets in MP May's sample were coded as Questioning authority, while 28% fall under the Name-calling/Gender insults category (see @tbl-liz_severity). @tbl-liz_account emphasizes that combined, Spammers and Anonymous accounts total nearly 80% of all accounts in MP May's networked public -- a significant number compared to the 19% of Personal accounts. Given MP May's decades of climate advocacy and personal popularity, a higher number of Personal accounts was anticipated, but the number of Spammers and Anonymous accounts could be explained by the changing platform affordances.

Although memes are not as prominent in MP May's sample of Tweets, user-generated alternative science infographics and links to alternative science YouTube videos and websites repeatedly appeared. Tweets presenting alternative science were often coded as Questioning authority due to the tone and use of demeaning language, as seen in @tbl-acidrain-example. Instead of having an entirely civil conversation, MP May's grasp of science and qualifications is challenged.

| Tweet                                                                  |
|------------------------------------------------------------------------|
| \@ElizabethMay Do you remember the acid rain crisis - just about killed us all; then the ozone hole..how we survived? And the ice caps melting..good thing coast didn’t get submersed.  Now this time can you show legitimate science? No hey? Weird, climatologists have expertise that disagrees |

: Sample of a Tweet **Questioning authority** sent to MP May. {#tbl-acidrain-example}

## Laurel Collins

Tweets in MP Collins' sample, for both severity of harassment and type of account were generally more severe than I originally hypothesized. I expected to see a fairly even split between Tweets coded as Questioning authority and Neutral, but ultimately 75% of Tweets were coded as Questioning authority and just 8% as Neutral (see @tbl-laurel_severity). Unlike DPM Freeland and MP May, the number of MP Collins Tweets categorized as Name-calling/Gender insults is much lower (at 13%), but there are more Tweets coded as Vicious language, Credible threats, and Hate speech when compared to MP May. For type of account, MP Collins had the highest number of Personal accounts at 27%, the third most chosen category behind Spammers and Anonymous accounts (as shown in @tbl-laurel_account).

Moreover, I identified qualitative differences in the word choice and tone used in replies to MP Collins. @tbl-mydear-example illustrates the use of patriarchal and paternalistic language directed toward MP Collins, with the use of "my dear". In addition to talking down the qualifications of MP Collins, this user also questions climate science (offering up the popular alternative science suggestion that arson is responsible for forest fires) and voting behaviours in British Columbia. Tweets like this one and others in MP Collins' sample continue to emphasize the microaggressions faced by female politicians as they communicate about consequential policy issues [@harmer; @mediatingmisogyny].

| Tweet                                                                  |
|------------------------------------------------------------------------|
| \@Laurel_BC \@thenarwhalca Arson my dear. Not climate, CRIMINAL. What the fck is wrong with BC they keep voting NDP. Seriously!? |

: Sample of a Tweet containing **Name-calling/Gender insults** sent to MP Collins. {#tbl-mydear-example}

## Deliberative Democracy

Of the three politicians, MP May's Twitter account best fulfills the definition of deliberative democracy previously outlined, having open conversations with multiple view points and two way flows of communication (despite 55% of her Tweets being coded as Questioning authority). All viewpoints, including both the fact Canada is not going far enough on climate action and is going too far (especially with carbon pricing) features prominently through the sample of Tweets. Among the users who believe and promote alternative facts, some claim climate change is simply changing weather, or that forest fires are caused by arson, or other niche reasons supported by user-generated websites. Although over 80% of the Tweets in her sample were coded as either Questioning authority or Name-calling/gender insults, people in MP May's networked public more frequently discussed science and policy, albeit sometimes alternative science and facts. MP Collins' networked public also possessed these characteristics, although she was less willing to engage by responding. DPM Freeland received significant amounts of verbal backlash (reinforcing research conducted by @stopfner) and her staff intentionally did not response to replies from the public, meaning her Twitter account is more a space to broadcast political messages instead of engaging in open and constructive discourse with the public [@marland; @small2016]. The lack of two-way discussion, possibly due to DPM Freeland's status and sheer volume of Tweets and replies from the public, is unhealthy for democratic discourse. Although all three politicians could be using their Twitter accounts to more actively engage with the public, the waning engagement is understandable given Twitter's current state. Other more traditional means of two-way dialogue between elected officials and the public, such as town halls and constituent correspondence remain important ways to maintain a deliberative democracy with overwhelming online harassment.

## Limitations

Twitter's ever-changing affordances and focuses as a platform (such as promoting "free speech") directly and indirectly impact the severity of harassment and types of accounts deemed acceptable to keep on the platform. Many of the third-party tools, such as Botometer [@botometer], which previously assisted computational social science researchers in determining types of accounts have been rendered unusable with Twitter API changes, limiting my ability to determine which accounts in my study are bots. Consequently, the number of accounts categorized as bots in my study is likely smaller than the actual number of bots. It is impossible to know on a granular level how every change to Twitter affordances impacts each harassing Tweet and account on the platform, but can generally inform hypotheses and patterns established when analyzing the data.

Given the in-progress nature of this study, only one coder has coded all the Tweets so far, meaning there is no intercoder reliability. Following the methods outlined by @krippendorff, two additional coders will code a subset of Tweets, before statistically measuring intercoder agreement using `krippendorffsalpha` [@krippendorffsalpha].

# Conclusion

In this paper, I examined Tweets explicitly discussing climate change and environmental policy sent to DPM Freeland, MP May, and MP Collins to measure the severity of harassment on a seven-point scale and type of accounts behind the Tweets. My results reveal that over 85% of Tweets sent to the three politicians contained some level of harassment. My model identified and predicted nearly no quantitative differences between Tweets sent to all three female politicians. Spammer and Anonymous accounts were most frequently associated with engaging with the female politicians on Twitter and being responsible for sending the more serve forms of harassment identified. The Tweets analyzed for this study generally matched the criteria of what constitutes healthy democratic discourse, with users with multiple, diverse viewpoints weighing in on the issue of climate change. In future iterations of this study, attention will be turned toward ensuring intercoder reliability, gleaning a better understanding of the frequency of words used in harassing Tweets by doing topic modeling using Latent Dirichlet Allocation, and using LLMs to detect harassment. It is crucial to ensure we continue studying and discussing the intersection of climate change denialism and misogyny, because if we cannot mediate the risks of gendertrolling at the highest echelons of power, then female politicians may self-censor and risk everyone's ability to engage in respectful discourse surrounding climate change [@mediatingmisogyny].

# Acknowledgments {.unnumbered}
I am grateful for Rohan Alexander's helpful suggestions and feedback on drafts of this paper. This research is supported in part by funding from the Social Sciences and Humanities Research Council of Canada (Canada Graduate Scholarship - Master's) and Government of Ontario (Ontario Graduate Scholarship).

# Appendix {.unnumbered}

  - My codebook is available [here](https://github.com/InessaDeAngelis/torrential_twitter_bell_conf/blob/main/Inputs/Codebook.pdf)

  - My coding form is available [here](https://forms.gle/Limy51uAcvM3B7K66)

# References

### 2024-01-09 Scripts/02-clean_raw_Laurel_data.R

@@ -1094,5 +1094,5 @@ cleaned_laurel_tweets
 final_cleaned_laurel_tweets <- filter(cleaned_laurel_tweets, User_id != "2167166754")   
 final_cleaned_laurel_tweets
 
-# After allllll those steps, save Tweets to test before manually coding! #
+# Save Tweets #
 write_csv(x = final_cleaned_laurel_tweets, file = "Outputs/Data/Laurel/final_cleaned_laurel_tweets.csv")

### 2024-01-09 Scripts/03-test_raw_Chrystia_data.R

@@ -40,4 +40,4 @@ out <-
 summary(out)
 
 # Check number of rows is correct #
-nrow(cleaned_chrystia_tweets) == 2408
+nrow(cleaned_chrystia_tweets) == 2401

### 2024-01-09 Scripts/05-test_cleaned_coded_tweets.R

@@ -5,7 +5,7 @@
 # Contact: inessa.deangelis@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites
-  # 01-clean_coded_tweets.R
+  # 04-clean_coded_tweets.R
 
 #### Workspace setup ####
 library(testthat)
@@ -27,5 +27,5 @@ test_that("check class" , {
 })
 
 test_that("Check number of observations is correct", {
-  expect_equal(nrow(finalized_cleaned_tweets), 4100)
+  expect_equal(nrow(finalized_cleaned_tweets), 4139)
 })

### 2024-01-13 Outputs/Presentation/bell_conference_slides.qmd
update slides

@@
 ## Background {background-color="#CBD6BE"}
-- Harassment on Twitter is well-documented
+- Harassment of female politicians is well-documented (Wagner, 2020; Erikson et al., 2023)
+- Intersection between climate change denialism and misogyny (Anshelm & Hultman, 2014)
+- Networked publics impact speech in the digital public sphere (boyd, 2010; Bruns, 2023)
+
+## Theoretical Framework {background-color="#CBD6BE"}
+- Theory of Deliberative Democracy
+- Credited to Jürgen Habermas and Richard Sennet
+- View on a scale; "to what extent" (Rossini, 2022)
+
+## Research Questions {background-color="#CBD6BE"}
+  1. What is the severity of harassment female politicians receive when Tweeting about climate change, the environment, or related topics?
+  2. What types of accounts send harassing Tweets to female politicians?
+
+## Hypotheses {background-color="#CBD6BE"}
+  1. Evidence of harassment will be detected in replies to Tweets that discuss climate change, the environment, or related topics.
+  2. Personal and Anonymous accounts belonging to right-wing and ideologically-driven users will send Tweets containing the most harassment to the female politicians.
+
+## Methods {background-color="#CBD6BE"}
+- Statistical programming software `R` (R Core Team, 2023)
+- R Package for collecting Twitter threaded conversations: `voson.tcn` (Gertzel, 2021)
+- Manual coding using a Google Form
+
+## My Sample {background-color="#CBD6BE"}
 
 ```{r}
+# Set up #
 library(tidyverse)
@@
 # Read in the data #
-finalized_cleaned_tweets_anon <- read_csv(here::here("Outputs/Data/finalized_cleaned_tweets_anon.csv"))
+finalized_cleaned_tweets <- read_csv(here::here("Outputs/Data/finalized_cleaned_tweets.csv"))
 show_col_types = FALSE
@@
 
-finalized_cleaned_tweets_anon |>
+finalized_cleaned_tweets |>
   group_by(name_of_politician) |>
@@
     col.names = c("Name of Politician", "Number of Replies", "Percentage"),
-    booktabs = TRUE,
-  )
+    booktabs = TRUE) |>
+  kable_styling(font_size = 30) 
+```
 
-````
+## Severity of Harassment {background-color="#CBD6BE"}
+  1. Positive
+  2. Neutral
+  3. Questioning authority
+  4. Name-calling/Gender insults
+  5. Vicious language
+  6. Credible threats
+  7. Hate speech
+
+## Type of Account {background-color="#CBD6BE"}
+  1. Personal
+  2. Professional
+  3. Bots
+  4. Spammers
+  5. Anonymous
+  6. Suspended/deleted
+
+## Bayesian Hierarchical Model {background-color="#CBD6BE"}
+::: {.r-fit-text}
+$$
+\begin{aligned}
+y_i|\pi_i & \sim \mbox{Bern}(\pi_i) \\
+\mbox{logit}(\pi_i) & = \beta_0 + \alpha_{a[i]}^{\mbox{account}} + \alpha_{p[i]}^{\mbox{politician}} + \alpha_{v[i]}^{\mbox{verified}} \\
+\alpha_0 & \sim \mbox{Normal}(0, 2.5)\\
+\alpha_{a}^{\mbox{acc}} & \sim \mbox{Normal}\left(0, \sigma^2_{\mbox{acc}}\right)\mbox{ for }a = 1, 2, \dots, A\\
+\alpha_{p}^{\mbox{pol}} & \sim \mbox{Normal}\left(0, \sigma^2_{\mbox{pol}}\right)\mbox{ for }p = 1, 2, 3, P\\
+\alpha_{v}^{\mbox{ver}} & \sim \mbox{Normal}\left(0, \sigma^2_{\mbox{ver}}\right)\mbox{ for }v = 0, 1, V\\
+\sigma_{\mbox{acc}} & \sim \mbox{Exponential}(1)\\
+\sigma_{\mbox{pol}} & \sim \mbox{Exponential}(1) \\
+\sigma_{\mbox{ver}} & \sim \mbox{Exponential}(1)
+\end{aligned}
+$$
+:::
+
+## Results (Model) {background-color="#CBD6BE"}
+```{r}
+#| message: false
+#| eval: true
+#| echo: false
+#| label: fig-plotted
+#| fig-cap: Predicting whether a Tweet contains harassment or not, on the basis of the type of account behind the Tweet, which politician the Tweet was in response to, and whether a user is verified.
+#| warning: false
+
+library(marginaleffects)
+library(tidyverse)
+
+harassment_model <- readRDS(here::here("Outputs/Model/harassment_model.rds"))
+
+harassment_model_predictions <-
+  predictions(harassment_model)
+
+harassment_model_predictions |>
+  ggplot(aes(x = harassment_binary, y = estimate, color = name_of_politician)) +
+  geom_jitter(width = 0.2, height = 0.0, alpha = 0.3) +
+  labs(
+    x = "Harassment",
+    y = "Estimated probability that a Tweet contains harassment",
+    color = "Name of Politician"
+  ) +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 8)) + 
+  theme(axis.text.y = element_text(size = 8)) + 
+  theme(axis.title.y = element_text(size = 8)) +
+  theme(legend.position = "bottom") +
+  theme(legend.text = element_text(size = 6)) +
+  theme(legend.title = element_text(size = 9))
+
+```
+
+## Results (Coding) {background-color="#CBD6BE"}
+::: {.r-fit-text}
+```{r}
+# Kable font size fix code from: https://bookdown.org/yihui/rmarkdown-cookbook/kableextra.html
+# Set up #
+library(tidyverse)
+library(knitr)
+library(kableExtra)
+library(ggplot2)
+library(formattable)
+library(here)
+
+# Read in the data #
+finalized_cleaned_tweets <- read_csv(here::here("Outputs/Data/finalized_cleaned_tweets.csv"))
+show_col_types = FALSE
+
+#| message: false
+#| eval: true
+#| echo: false
+#| label: tbl-breakdown
+#| tbl-cap: X
+
+finalized_cleaned_tweets |>
+  group_by(severity_of_harassment) |>
+  count() |>
+  ungroup() |>
+  mutate(pct = paste0(round((n / sum(n)) * 100), "%")) |>
+  arrange(match(severity_of_harassment, c('Positive', 'Neutral', 'Questioning Authority', 'Name-calling/Gender insults', 'Vicious language', 'Credible threats', 'Hate speech'))) |>
+  kable(
+    col.names = c("Severity of Harassment", "Number of Replies", "Percentage"),
+    booktabs = TRUE) |>
+  kable_styling(font_size = 30)
+
+```
+:::
+
+## Results (Coding) {background-color="#CBD6BE"}
+::: {.r-fit-text}
+```{r}
+# Set up #
+library(tidyverse)
+library(knitr)
+library(kableExtra)
+library(ggplot2)
+library(formattable)
+library(here)
+
+# Read in the data #
+finalized_cleaned_tweets <- read_csv(here::here("Outputs/Data/finalized_cleaned_tweets.csv"))
+show_col_types = FALSE
+
+#| message: false
+#| eval: true
+#| echo: false
+#| label: tbl-breakdown2
+#| tbl-cap: X
+
+finalized_cleaned_tweets |>
+  group_by(type_of_account) |>
+  count() |>
+  ungroup() |>
+  mutate(pct = paste0(round((n / sum(n)) * 100), "%")) |>
+  arrange(match(type_of_account, c('Personal', 'Professional', 'Bots', 'Spammers', 'Anonymous', 'Suspended/deleted'))) |>
+  kable(
+    col.names = c("Type of Account", "Number of Accounts", "Percentage"),
+    booktabs = TRUE) |>
+  kable_styling(font_size = 30)
+
+```
+:::
+
+## Discussion: Questioning Authority {background-color="#CBD6BE"}
+| Tweet                                                                  |
+|------------------------------------------------------------------------|
+| \@ElizabethMay Do you remember the acid rain crisis - just about killed us all; then the ozone hole..how we survived?
+And the ice caps melting..good thing coast didn’t get submersed.
+Now this time can you show legitimate science?
+No hey?
+Weird, climatologists have expertise that disagrees |
+
+: A Tweet categorized as **Questioning authority** sent to MP May.
+
+## Discussion: Type of Accounts {background-color="#CBD6BE"}
+- More Spammers and Anonymous accounts than anticipated
+- Fewer Suspended/deleted accounts 
+- Professional accounts often belonged to Federal Conservative MPs
+
+## Discussion: Hate Speech {background-color="#CBD6BE"}
+
+![Example of a reply to a Tweet sent by DPM Freeland which revives historical photographs through memes and contains **Hate Speech**](hate_speech_example.png){width="400"}
+
+## Deliberative Democracy {background-color="#CBD6BE"}
+- MP May's account best fulfills the definition
+- MP Collins' account mostly fulfills the definition 
+- DPM Freeland's account does not
+
+## Why this matters {background-color="#CBD6BE"}
+- Future of democratic conversations online
+- We cannot let female politicians self-censor or be deterred from running for office 
+- Issue salience: continued conversations about climate change in traditional and social media
+
+## Thank You {background-color="#CBD6BE" .smaller}
+- Code, select data, and paper available: <https://github.com/InessaDeAngelis/torrential_twitter_bell_conf>
+- Questions, comments, and feedback welcome: <Inessa.DeAngelis@mail.utoronto.ca> 
+- Find me on GitHub & Twitter: **\@InessaDeAngelis**

### 2024-01-16 Outputs/Presentation/bell_conference_slides.qmd
update slides

@@
 format:
-  revealjs
+  revealjs:
+    slide-number: true
 title-slide-attributes: 
@@
 ---
+
+## Key Findings {background-color="#CBD6BE"}
+- 86% of Tweets contained some form of harassment 
+- Identified clear violations of Twitter’s Rules and Policies  
+- Threat to female politicians and the future of online democratic conversations
 
@@
 
+## Sample Tweet: Questioning Authority {background-color="#CBD6BE"}
+| Tweet                                                                  |
+|------------------------------------------------------------------------|
+| \@ElizabethMay Do you remember the acid rain crisis - just about killed us all; then the ozone hole..how we survived?
+And the ice caps melting..good thing coast didn’t get submersed.
+Now this time can you show legitimate science?
+No hey?
+Weird, climatologists have expertise that disagrees |
+
+: A Tweet categorized as **Questioning authority** sent to MP May.
+
+## Sample Tweet: Name-calling/Gender insults {background-color="#CBD6BE"}
+| Tweet                                                                  |
+|------------------------------------------------------------------------|
+| \@Laurel_BC \@thenarwhalca Arson my dear. Not climate, CRIMINAL. What the 🤬 is wrong with BC they keep voting NDP. Seriously!? 🤦🏻‍♀️ |
+
+: A **Name-calling/Gender insults** Tweet sent to MP Collins.
+
 ## Type of Account {background-color="#CBD6BE"}
@@
 y_i|\pi_i & \sim \mbox{Bern}(\pi_i) \\
-\mbox{logit}(\pi_i) & = \beta_0 + \alpha_{a[i]}^{\mbox{account}} + \alpha_{p[i]}^{\mbox{politician}} + \alpha_{v[i]}^{\mbox{verified}} \\
-\alpha_0 & \sim \mbox{Normal}(0, 2.5)\\
-\alpha_{a}^{\mbox{acc}} & \sim \mbox{Normal}\left(0, \sigma^2_{\mbox{acc}}\right)\mbox{ for }a = 1, 2, \dots, A\\
-\alpha_{p}^{\mbox{pol}} & \sim \mbox{Normal}\left(0, \sigma^2_{\mbox{pol}}\right)\mbox{ for }p = 1, 2, 3, P\\
-\alpha_{v}^{\mbox{ver}} & \sim \mbox{Normal}\left(0, \sigma^2_{\mbox{ver}}\right)\mbox{ for }v = 0, 1, V\\
-\sigma_{\mbox{acc}} & \sim \mbox{Exponential}(1)\\
-\sigma_{\mbox{pol}} & \sim \mbox{Exponential}(1) \\
-\sigma_{\mbox{ver}} & \sim \mbox{Exponential}(1)
+\mbox{logit}(\pi_i) & = \beta_0 + \alpha_{a[i]}^{\mbox{account}} + \alpha_{p[i]}^{\mbox{politician}} + \alpha_{v[i]}^{\mbox{verified}}
 \end{aligned}
@@
   ggplot(aes(x = harassment_binary, y = estimate, color = name_of_politician)) +
-  geom_jitter(width = 0.2, height = 0.0, alpha = 0.3) +
+  geom_jitter(width = 0.2, height = 0.01, alpha = 0.3) +
   labs(
     x = "Harassment",
-    y = "Estimated probability that a Tweet contains harassment",
+    y = "Estimated probability that a \nTweet contains harassment",
     color = "Name of Politician"
@@
   theme_classic() +
-  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 8)) + 
-  theme(axis.text.y = element_text(size = 8)) + 
-  theme(axis.title.y = element_text(size = 8)) +
+  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 14)) + 
+  theme(axis.text.y = element_text(size = 14)) + 
+  theme(axis.text.x = element_text(size = 14)) +
+  theme(axis.title.y = element_text(size = 20)) +
+  theme(axis.title.x = element_text(size = 20)) +
   theme(legend.position = "bottom") +
-  theme(legend.text = element_text(size = 6)) +
-  theme(legend.title = element_text(size = 9))
+  theme(legend.text = element_text(size = 12)) +
+  theme(legend.title = element_text(size = 16))
 
@@
 ## Discussion: Questioning Authority {background-color="#CBD6BE"}
-| Tweet                                                                  |
-|------------------------------------------------------------------------|
-| \@ElizabethMay Do you remember the acid rain crisis - just about killed us all; then the ozone hole..how we survived?
-And the ice caps melting..good thing coast didn’t get submersed.
-Now this time can you show legitimate science?
-No hey?
-Weird, climatologists have expertise that disagrees |
-
-: A Tweet categorized as **Questioning authority** sent to MP May.
+- 55% of Tweets were categorized as Questioning authority 
+- Not information-seeking questions or an accountability mechanism 
+- Focused on undermining and discrediting
 
@@
 
-## Why this matters {background-color="#CBD6BE"}
+## Limitations {background-color="#CBD6BE"}
+- Not representative of the larger public (Bermingham & Smeaton, 2011)
+- Twitter promotes the most active and polarized users (McGregor, 2020)
+- Ever-changing platform affordances 
+- No intercoder reliability yet (Krippendorff, 2013)
+
+## Why This Matters {background-color="#CBD6BE"}
 - Future of democratic conversations online

### 2024-01-25 Outputs/Paper/Publication_version/paper_for_pub.qmd
start editing for publication

--- 2024-01-09 Outputs/Paper/Bell_Conference_Paper.qmd
@@
 ---
-title: "Torrential Twitter: Climate Change, Female Politicians, and Harassment"
+title: "Torrential Twitter? Measuring the Severity of Harassment when Canadian Female Politicians Tweet about Climate Change"
 author: "Inessa De Angelis^[Faculty of Information, University of Toronto, Inessa.DeAngelis@mail.utoronto.ca]"
@@
 date-format: "long"
-abstract: "Women in politics face considerable harassment.
+abstract: "Research has shown that women in politics face considerable harassment.
 Known as “gendertrolling,” this harassment is part of a global trend of violence against women in politics.
-There are many significant previously documented cases of gendertrolling on public social media platforms such as Twitter.
-Framed through the theory of deliberative democracy, this study conducts quantitative content analysis on the replies received by three female politicians in Canada when Tweeting about climate change and the environment.
-These politicians are Deputy Prime Minister Chrystia Freeland (from the Liberal Party), Elizabeth May (co-Leader of the Green Party), and Laurel Collins (from the New Democratic Party).
+This study investigates the severity of harassment three Canadian female politicians receive when Tweeting about climate change and the types of accounts behind the replies.
+Results from the quantitative content analysis reveal that 86% of Tweets contained some form of harassment.
 I then built a Bayesian hierarchical model to investigate the relationship between the severity of harassment and the type of account that a user has.
-The majority of replies contain some form of harassment, often questioning authority or name-calling/gender insults, and come from users that have spam or anonymous accounts.
+The results from my model suggest that despite differences in political affiliation and status, the three politicians are equally impacted by harassment when Tweeting about climate change.
 *This paper contains language and themes that some readers may find offensive.*"
@@
 number-sections: true
-bibliography: conference_references.bib
+bibliography: publication_references.bib
 csl: apa.csl
@@
 
-<!-- The past few decades have led to structural transformation and fragmentation of the idea of the public sphere, moving from having a singular, "official" public sphere to a multitude of smaller parallel ones, called "subaltern counterpublics" and networked publics mediated by technological affordances [@brunshighfield; @fraser1991; @boyd2010].
-Technology reorganized the flow of information in society, distinguishing networked publics from subaltern counterpublics and the "official" public.
-Discourse traditionally happened in mediated spaces, but the rise of social media allows it to happen everywhere and is theoretically breaking down barriers of who has access to the walled garden of democratic discourse [@mediatingmisogyny; @trifiro].
-Despite the potential formation of new publics online, the public which continues to deny the existence of climate change are largely white, male, and Christian and have free time (often dictated by patriarchal norms) to troll female politicians on Twitter whose actions as climate leaders do not fit traditional gender roles and conceptions of power [@Anshelm; @mccrightdunlap; @degeus; @mantilla2013].
-Networked publics can be potent for democracy, undermining the authority of female politicians and risking the civility of democratic discourse.
-Consequently, women have and continue to be on the margins of the public sphere, both in physical spaces like the House of Commons and online, as underscored by an @ipu global survey which found that 82% of female politicians reported being subjected to psychological violence (including harassment, threats, and sexist comments).
-In Canada, specific examples of on-going marginalization can be seen through the lived realities of women in politics, with only one female Prime Minister, Rt.
-Hon.
-Kim Campbell in 1993, and in 2024, only 30% of MPs are female [@degeus; @hoc].
--->
-
 The past few decades have led to the structural transformation and fragmentation of the public sphere, moving from having a singular, "official" public sphere to a multitude of parallel smaller ones, called "subaltern counterpublics" and networked publics mediated by technological affordances [@brunshighfield; @fraser1991; @boyd2010].
@@
 @mckaytenove highlight that a new characteristic of deliberative democracy is the ability for those who participate in debate to do so in anonymous and pseudonymous ways, which both strengthen and undermine deliberation in different ways.
-
-<!-- Diverging scholarly viewpoints exist when operationalizing and applying the theory of deliberative democracy.
-Some scholars view the theory in rigid terms, evaluating all characteristics and scenarios, such as political parties, systems, and institutions on a "yes" or "no" basis [@sokolon].
-Sometimes, other scholars overlook or discount the role of social media and emerging technologies in creating networked publics which can drastically shape the quality and quantity of online democratic discourse.
-Moreover, other scholars view the theory of deliberative democracy on a scale - looking at the extent in which healthy democratic speech exists in specific contexts [@rossini].
-Communication and media studies scholars are concerned about the nuances of discourse and the specific contexts in which it is situated and how algorithms and platform affordances are building and shaping these contexts [@bruns2023].
--->
 
@@
 
-After manually coding the 4,139 Tweets using my Google Form and Codebook (see [Appendix]), I proceeded to the second round of cleaning the Tweets using R [@r].
+After manually coding the 4,139 Tweets using my Codebook (see [Appendix]), I proceeded to the second round of cleaning.
 I eliminated columns of data which were useful for determining the type of account but not relevant for the next steps of my analysis.
@@
 I tested the cleaned data using `validate` [@validate], primarily validating variable types and ensuring the number of rows in the dataset matches the number of Tweets I coded.
-I then analyzed and visualized my data in R [@r], using functions from `knitr` [@rknitr], `kableExtra` [@rKableExtra], `Formattable` [@rFormattable], and `ggplot2` [@rGgplot2].
+I then analyzed and visualized my data using functions from `knitr` [@rknitr], `kableExtra` [@rKableExtra], `Formattable` [@rFormattable], and `ggplot2` [@rGgplot2].
 
@@
 
+# Declaration of Conflicting Interests {.unnumbered}
+The author declares no potential conflicts of interest with respect to the research, authorship, and/or publication of this article.
+
 # Acknowledgments {.unnumbered}
-I am grateful for Rohan Alexander's helpful suggestions and feedback on drafts of this paper.
-This research is supported in part by funding from the Social Sciences and Humanities Research Council of Canada (Canada Graduate Scholarship - Master's) and Government of Ontario (Ontario Graduate Scholarship).
+I am grateful for Rohan Alexander's helpful suggestions and feedback on drafts of this paper and for Elizabeth Dubois' guidance during the early conception of this study.
+Thank you to Sarah Xie and Allyson Cui for their research assistance.
+
+# Funding {.unnumbered}
+The author discloses receipt of the following financial support for the research, authorship, and/or publication of this article: This study was funded by the Social Sciences and Humanities Research Council of Canada, Canada Graduate Scholarship (id: 766-2022-0719) and the Government of Ontario, *2023-2024 Ontario Graduate Scholarship*.
 
@@
 
-  - My coding form is available [here](https://forms.gle/Limy51uAcvM3B7K66)
-
 # References

### 2024-02-03 Outputs/Paper/Publication_version/paper_for_pub.qmd
small edits

@@
 date-format: "long"
-abstract: "Research has shown that women in politics face considerable harassment.
-Known as “gendertrolling,” this harassment is part of a global trend of violence against women in politics.
-This study investigates the severity of harassment three Canadian female politicians receive when Tweeting about climate change and the types of accounts behind the replies.
-Results from the quantitative content analysis reveal that 86% of Tweets contained some form of harassment.
+abstract: "Research has shown that women in politics face considerable online harassment know as “gendertrolling.” This study investigates the severity of harassment three Canadian female politicians receive when Tweeting about climate change and the types of accounts behind the replies.
+All replies to climate and environmental focused Tweets posted by the politicians from September 2022 to October 2023 were collected for quantitative content analysis.
+Results from my content analysis reveal that 86% of Tweets contained some form of harassment.
 I then built a Bayesian hierarchical model to investigate the relationship between the severity of harassment and the type of account that a user has.
@@
 "F\*CK OFF WITH YOUR CLIMATE SCAM ..
-nazi traitor b!tch," reads a reply sent to a Tweet about climate change that originated on the account of Canada's Deputy Prime Minister (DPM) and Minister of Finance, the Honourable Chrystia Freeland.
+nazi traitor b!tch," reads a reply sent to a Tweet[^1] about climate change that originated on the account of Canada's Deputy Prime Minister (DPM) and Minister of Finance, the Honourable Chrystia Freeland.
 For DPM Freeland and women across all political parties and levels of government in Canada and other democratic nations, coping with online and offline harassment is a reality of serving as an elected official [@southern; @silencingwomen].
@@
 Female politicians who adopt strong policy stances are more likely to face online misogyny and harassment because it is not consistent with existing gender stereotypes and notions of power and poses a threat to male climate deniers [@courtemanche; @rheault; @degeus].
+
+[^1]: In July 2023, CEO Elon Musk announced that Twitter would be renamed to X. This paper will continue to call the platform Twitter.
 
@@
 
-Type of account is defined as the dynamics of relationships between followers, followings, and lists and will be determined by analyzing the accounts' bio, profile image, and other characteristics [@singh; @uddin].
+Type of account is defined as the dynamics of relationships between followers, followings, and lists and will be determined by analysing the accounts' bio, profile image, and other characteristics [@singh; @uddin].
 Types of accounts include:
@@
 
-By employing the theory of deliberative democracy, this paper analyzes responses to Tweets sent by female politicians which explicitly discuss climate change and environmental policy to evaluate the extent at which they fulfill the characteristics of healthy democratic discourse.
+By employing the theory of deliberative democracy, this paper analyses responses to Tweets sent by female politicians which explicitly discuss climate change and environmental policy to evaluate the extent at which they fulfill the characteristics of healthy democratic discourse.
 Often paired with their work on the public sphere, Jürgen Habermas and Richard Sennet are credited for publishing founding research on the theory of deliberative democracy [@kies2010].
@@
 My sample includes any original Tweets written in English (no quote or Retweets) that originated on the accounts of DPM Freeland (\@cafreeland), MP May (\@elizabethmay), and MP Collins (\@laurel_bc) that were posted between September 1, 2022, and October 31, 2023.
-Tweets also had to the contain the word "climate,” "environment,” and/or "environmental" (as part of the text of the Tweet or as a hashtag).
+These three politicians were selected based on their pro-climate change stances, evidence of harassing Tweets, and diversity in regional representation and political affiliation.
+Only 6% of female MPs identify as a visible minority or Indigenous and do not frequently discuss climate change on Twitter, which is why my sample contains all white MPs [@hoc].
+Tweets also had to the contain the word "climate," "environment," and/or "environmental" (as part of the text of the Tweet or as a hashtag).
 For threaded Tweets sent by the politicians, the first Tweet of the thread had to contain at least one of the key words and the overall focus of the thread had to be on climate change and/or environmental policy.
@@
 Cleaning serves as a useful process for identifying anomalies in the dataset, such as mis-matched Tweets and account metadata.
-The `voson.tcn` package provided several columns of Twitter metadata that was not relevant to the objectives of this paper, so I eliminated those and focused on columns such as the text of the Tweet, the user's location, bio, profile picture, and whether they paid to be verified with a blue checkmark through Twitter's subscription program.
+I eliminated columns of metadata unrelated to this study and focused on columns such as the text of the Tweet, the user's location, bio, profile picture, and whether they paid to be verified with a blue checkmark through Twitter's subscription program.
 All raw and coded data cleaning was done using R [@r], utilizing functions from the `tidyverse` [@rTidyverse] and `janitor` [@rJanitor].
@@
 I tested the cleaned data using `validate` [@validate], primarily validating variable types and ensuring the number of rows in the dataset matches the number of Tweets I coded.
-I then analyzed and visualized my data using functions from `knitr` [@rknitr], `kableExtra` [@rKableExtra], `Formattable` [@rFormattable], and `ggplot2` [@rGgplot2].
+I then analysed and visualized my data using functions from `knitr` [@rknitr], `kableExtra` [@rKableExtra], `Formattable` [@rFormattable], and `ggplot2` [@rGgplot2].
 
@@
 Consequently, the number of accounts categorized as bots in my study is likely smaller than the actual number of bots.
-It is impossible to know on a granular level how every change to Twitter affordances impacts each harassing Tweet and account on the platform, but can generally inform hypotheses and patterns established when analyzing the data.
-
-Given the in-progress nature of this study, only one coder has coded all the Tweets so far, meaning there is no intercoder reliability.
-Following the methods outlined by @krippendorff, two additional coders will code a subset of Tweets, before statistically measuring intercoder agreement using `krippendorffsalpha` [@krippendorffsalpha].
+It is impossible to know on a granular level how every change to Twitter affordances impacts each harassing Tweet and account on the platform, but can generally inform hypotheses and patterns established when analysing the data.
 
@@
 Spammer and Anonymous accounts were most frequently associated with engaging with the female politicians on Twitter and being responsible for sending the more serve forms of harassment identified.
-The Tweets analyzed for this study generally matched the criteria of what constitutes healthy democratic discourse, with users with multiple, diverse viewpoints weighing in on the issue of climate change.
-In future iterations of this study, attention will be turned toward ensuring intercoder reliability, gleaning a better understanding of the frequency of words used in harassing Tweets by doing topic modeling using Latent Dirichlet Allocation, and using LLMs to detect harassment.
+The Tweets analysed for this study generally matched the criteria of what constitutes healthy democratic discourse, with users with multiple, diverse viewpoints weighing in on the issue of climate change.
+In future iterations of this study, attention will be turned toward using LLMs to detect nauanced forms of harassment.
 It is crucial to ensure we continue studying and discussing the intersection of climate change denialism and misogyny, because if we cannot mediate the risks of gendertrolling at the highest echelons of power, then female politicians may self-censor and risk everyone's ability to engage in respectful discourse surrounding climate change [@mediatingmisogyny].
 
-# Declaration of Conflicting Interests {.unnumbered}
-The author declares no potential conflicts of interest with respect to the research, authorship, and/or publication of this article.
-
 # Acknowledgments {.unnumbered}
-I am grateful for Rohan Alexander's helpful suggestions and feedback on drafts of this paper and for Elizabeth Dubois' guidance during the early conception of this study.
-Thank you to Sarah Xie and Allyson Cui for their research assistance.
+The author(s) thank(s) Rohan Alexander for the helpful suggestions and feedback on drafts of this paper and Elizabeth Dubois for guidance during the early conception of this study.
+The author(s) also thank(s) Sarah Xie and Allyson Cui for their research assistance.
 
 # Funding {.unnumbered}
-The author discloses receipt of the following financial support for the research, authorship, and/or publication of this article: This study was funded by the Social Sciences and Humanities Research Council of Canada, Canada Graduate Scholarship (id: 766-2022-0719) and the Government of Ontario, *2023-2024 Ontario Graduate Scholarship*.
+The author(s) disclose(s) receipt of the following financial support for the research, authorship, and/or publication of this article: This study was funded by the Social Sciences and Humanities Research Council of Canada (grant ID: 766-2022-0719) and the Government of Ontario, *2023-2024 Ontario Graduate Scholarship*.
 
-# Appendix {.unnumbered}
-
-  - My codebook is available [here](https://github.com/InessaDeAngelis/torrential_twitter_bell_conf/blob/main/Inputs/Codebook.pdf)
+# Declaration of Conflicting Interests {.unnumbered}
+The author(s) declare(s) that there is no conflict of interest.
 

### 2024-02-05 Outputs/Paper/Publication_version/paper_for_pub.qmd
coders & contributions

@@
 
-[^1]: In July 2023, CEO Elon Musk announced that Twitter would be renamed to X. This paper will continue to call the platform Twitter.
+[^1]: In July 2023, CEO Elon Musk announced that Twitter would be renamed to X. This paper continues to call the platform Twitter.
 
@@
 
-Type of account is defined as the dynamics of relationships between followers, followings, and lists and will be determined by analysing the accounts' bio, profile image, and other characteristics [@singh; @uddin].
+Type of account is defined as the dynamics of relationships between followers, followings, and lists and will be determined by analyzing the accounts' bio, profile image, and other characteristics [@singh; @uddin].
 Types of accounts include:
@@
 
-By employing the theory of deliberative democracy, this paper analyses responses to Tweets sent by female politicians which explicitly discuss climate change and environmental policy to evaluate the extent at which they fulfill the characteristics of healthy democratic discourse.
+By employing the theory of deliberative democracy, this paper analyzes responses to Tweets sent by female politicians which explicitly discuss climate change and environmental policy to evaluate the extent at which they fulfill the characteristics of healthy democratic discourse.
 Often paired with their work on the public sphere, Jürgen Habermas and Richard Sennet are credited for publishing founding research on the theory of deliberative democracy [@kies2010].
@@
 I eliminated columns of metadata unrelated to this study and focused on columns such as the text of the Tweet, the user's location, bio, profile picture, and whether they paid to be verified with a blue checkmark through Twitter's subscription program.
-All raw and coded data cleaning was done using R [@r], utilizing functions from the `tidyverse` [@rTidyverse] and `janitor` [@rJanitor].
+All raw and coded data cleaning was done using R.
 The original Tweets and replies sent by the female politicians in response to their own thread (known as a threaded Tweet) were omitted during the cleaning process.
@@
 I tested the cleaned data using `validate` [@validate], primarily validating variable types and ensuring the number of rows in the dataset matches the number of Tweets I coded.
-I then analysed and visualized my data using functions from `knitr` [@rknitr], `kableExtra` [@rKableExtra], `Formattable` [@rFormattable], and `ggplot2` [@rGgplot2].
+I then analyzed and visualized my data using functions from `knitr` [@rknitr], `kableExtra` [@rKableExtra], `Formattable` [@rFormattable], and `ggplot2` [@rGgplot2].
 
@@
 
-### Codebook
-
-I developed a comprehensive codebook building on previous research and a sample of Tweets (see [Appendix]).
+I developed a comprehensive codebook building on previous research and a sample of Tweets.
 Severity of harassment is coded on a seven-point scale, with the seven categories being: Positive, Neutral, Questioning authority, Name-calling/Gender insults, Vicious language, Credible threats, and Hate speech.
@@
 Through this study, I develop and test a new quantitative seven-point scale which contributes to on-going research by emphasizing everyday forms of harassment, such as microaggressions and questioning the authority of female politicians.
+My third category, Questioning authority, is a specific contribution, as it is a phenomenon recognized in the literature [@krook2020], but not typically included in coding schemes as a way to categorize harassment directed toward female politicians.
+
 These more everyday forms of harassment are often missed during binary coding conducted by large language models (LLMs).
 My seven-point scale also combines the nuance from previous qualitative projects which employ content analysis and interviews, while recognizing the benefits of more statistical and quantitative approaches offered by computational political communication researchers.
+
+To ensure intercoder reliability, an undergraduate research assistant coded a random selection of ten percent of the total number of Tweets in the sample.
+Intercoder reliability was calculated using the package `irr` [@irr] to check the extended percentage agreement among coders.
+Agreement for severity of harassment was 87.5%, while agreement for type of account was 76%.
+@lacy2015 suggest that results over 80% are acceptable and results between 67% and 80% are tentatively acceptable, with explanation (further discussed in [Limitations]).
 
@@
 MP Collins' networked public also possessed these characteristics, although she was less willing to engage by responding.
-DPM Freeland received significant amounts of verbal backlash (reinforcing research conducted by @stopfner) and her staff intentionally did not response to replies from the public, meaning her Twitter account is more a space to broadcast political messages instead of engaging in open and constructive discourse with the public [@marland; @small2016].
-The lack of two-way discussion, possibly due to DPM Freeland's status and sheer volume of Tweets and replies from the public, is unhealthy for democratic discourse.
+DPM Freeland received significant amounts of verbal backlash and her staff intentionally did not response to replies from the public, meaning her Twitter account is more a space to broadcast political messages instead of engaging in open and constructive discourse with the public [@marland; @small2016].
+The lack of two-way discussion, possibly due to DPM Freeland's status and sheer volume of Tweets and replies from the public, makes the digital public sphere situated around her account unhealthy for democratic discourse.
 Although all three politicians could be using their Twitter accounts to more actively engage with the public, the waning engagement is understandable given Twitter's current state.
-Other more traditional means of two-way dialogue between elected officials and the public, such as town halls and constituent correspondence remain important ways to maintain a deliberative democracy with overwhelming online harassment.
+Other more traditional means of two-way dialogue between elected officials and the public, such as town halls and constituent correspondence remain important ways to maintain deliberative democracy.
 
@@
 Twitter's ever-changing affordances and focuses as a platform (such as promoting "free speech") directly and indirectly impact the severity of harassment and types of accounts deemed acceptable to keep on the platform.
+The changing affordances likely contributed to the lower level of agreement for type of account between coders, given how frequently accounts are create, deleted, and suspended.
 Many of the third-party tools, such as Botometer [@botometer], which previously assisted computational social science researchers in determining types of accounts have been rendered unusable with Twitter API changes, limiting my ability to determine which accounts in my study are bots.
 Consequently, the number of accounts categorized as bots in my study is likely smaller than the actual number of bots.
-It is impossible to know on a granular level how every change to Twitter affordances impacts each harassing Tweet and account on the platform, but can generally inform hypotheses and patterns established when analysing the data.
+It is impossible to know on a granular level how every change to Twitter affordances impacts each harassing Tweet and account on the platform, but can generally inform hypotheses and patterns established when analyzing the data.
 
@@
 Spammer and Anonymous accounts were most frequently associated with engaging with the female politicians on Twitter and being responsible for sending the more serve forms of harassment identified.
-The Tweets analysed for this study generally matched the criteria of what constitutes healthy democratic discourse, with users with multiple, diverse viewpoints weighing in on the issue of climate change.
-In future iterations of this study, attention will be turned toward using LLMs to detect nauanced forms of harassment.
+The Tweets analyzed for this study generally matched the criteria of what constitutes healthy democratic discourse, with users with multiple, diverse viewpoints weighing in on the issue of climate change.
 It is crucial to ensure we continue studying and discussing the intersection of climate change denialism and misogyny, because if we cannot mediate the risks of gendertrolling at the highest echelons of power, then female politicians may self-censor and risk everyone's ability to engage in respectful discourse surrounding climate change [@mediatingmisogyny].

### 2024-02-07 Outputs/Paper/Publication_version/paper_for_pub.qmd
overhaul + details

@@
 
-"F\*CK OFF WITH YOUR CLIMATE SCAM ..
+"F\*CK OFF WITH YOUR CLIMATE SCAM...
 nazi traitor b!tch," reads a reply sent to a Tweet[^1] about climate change that originated on the account of Canada's Deputy Prime Minister (DPM) and Minister of Finance, the Honourable Chrystia Freeland.
-For DPM Freeland and women across all political parties and levels of government in Canada and other democratic nations, coping with online and offline harassment is a reality of serving as an elected official [@southern; @silencingwomen].
+For DPM Freeland and women across all political parties and levels of government in Canada and other democratic nations, coping with online and offline harassment is a reality of serving as an elected official [@southern; @trifiro].
 Known as "gendertrolling," this harassment is part of a global trend of violence against women [@mantilla2013; @wagner].
-Gender-based harassment on Twitter is well documented in academic literature and inexplicably pro-environmental behaviors are often viewed as "feminine" [@Citron; @mediatingmisogyny; @Anshelm].
+Gender-based harassment on Twitter is well documented in academic literature and, inexplicably, pro-environmental behaviors are often viewed as "feminine" [@Citron; @mediatingmisogyny; @Anshelm].
 Female politicians who adopt strong policy stances are more likely to face online misogyny and harassment because it is not consistent with existing gender stereotypes and notions of power and poses a threat to male climate deniers [@courtemanche; @rheault; @degeus].
@@
 
-To gain a deeper understanding of the intersection of climate change denialism and online gendered-harassment faced by Canadian female politicians, I measure the severity of harassment DPM and MP for University--Rosedale, Hon.
-Chrystia Freeland (from the Liberal Party), MP for Saanich--Gulf Islands, Elizabeth May (Co-Leader of the Green Party), and MP for Victoria, Laurel Collins (from the New Democratic Party) receive specifically when Tweeting about climate change and environmental policy on a seven-point scale and investigate the types of accounts behind the Tweets on a six-point scale.
-After manually coding Tweets to determine the severity of harassment and type of account, I then built a Bayesian hierarchical model to explore the relationship between the type of account, whether a user was verified through Twitter's subscription program, and which female politician the reply was directed toward to see whether certain combinations of these variables are more likely to lead to a reply which contains harassment.
-It is hypothesized that evidence of harassment will be detected in the replies and that Personal and Anonymous Twitter accounts belonging to right-wing and ideologically-driven users will send Tweets containing the most harassment to the female politicians.
-
-Harassment or gendertrolling is defined as sexist or misogynistic remarks that target a person based on their gender or sexuality and have varying levels of severity [@wagner].
-Severity of harassment includes:
-
-1.  Positive
-
-2.  Neutral
-
-3.  Questioning authority
-
-4.  Name-calling/Gender insults
-
-5.  Vicious language
-
-6.  Credible threats
-
-7.  Hate speech
-
-Type of account is defined as the dynamics of relationships between followers, followings, and lists and will be determined by analyzing the accounts' bio, profile image, and other characteristics [@singh; @uddin].
-Types of accounts include:
-
-1.  Personal
-
-2.  Professional
-
-3.  Bots
-
-4.  Spammers
-
-5.  Anonymous
-
-6.  Suspended/deleted
+To gain a deeper understanding of the intersection of climate change denialism and online gendered-harassment faced by Canadian female politicians, I collected and manually coded replies to Tweets from DPM and MP for University--Rosedale, Hon.
+Chrystia Freeland (from the Liberal Party), MP for Saanich--Gulf Islands, Elizabeth May (Co-Leader of the Green Party), and MP for Victoria, Laurel Collins (from the New Democratic Party) that specifically discuss climate change and environmental policy.
+Tweets were coded using a seven-point scale to measure the severity of harassment and a six-point scale to categorize the types of accounts behind the replies.
+I then built a Bayesian hierarchical model to explore the relationship between the type of account, whether a user was verified through Twitter's subscription program, and which female politician the reply was directed toward to see whether certain combinations of these variables are more likely to lead to a harassing reply.
 
 My analysis reveals that 86% of all replies to Tweets about climate change and environmental policy that originated on the accounts of DPM Freeland, MP May, and MP Collins contain some form of harassment, ranging from Questioning authority to Hate speech.
-The remaining 14% of Tweets had either positive or neutral sentiments.
 Questioning the authority of female politicians, followed by Name-calling/Gender insults were the most common forms of harassment identified, accounting for over 80% of all Tweets.
@@
 My Bayesian hierarchical model suggests that there are no significant quantitative differences between the severity of harassment received by the three politicians, although qualitative differences, including word choices and tone were detected during the coding process.
-My [Discussion] section further explores these qualitative and quantitative differences, among other key findings.
 
-In the remainder of this paper, I commence with the [Literature Review], followed by my [Theoretical Framework].
-Next, I discuss my [Data and Methods].
-Then, I highlight my [Results] and [Model], before providing further analysis and insights in the [Discussion] section.
-Finally, in the [Conclusion], I summarize my main findings.
+This study contributes to our knowledge of online harassment faced by female politicians by introducing a seven-point scale to measure the severity of harassment and a six-point scale to categorize the types of accounts behind the replies.
+The third category of harassment, questioning authority, is a specific contribution, as it is a phenomenon recognized in the literature [@krook2020], yet not typically included in coding schemes designed to measure harassment.
+Lastly, this study advances our understanding of the intersection between climate change denialism and online misogyny, revealing that the combination of the two areas is toxic for female politicians and democratic discourse.
 
@@
 
-## Twitter & The Digital Public Sphere
+## Twitter & The Digital Public Sphere {.unnumbered}
 
@@
 Discourse traditionally happened in mediated spaces, but the rise of social media allows it to happen everywhere, theoretically breaking down barriers of who has access to the walled garden of democratic discourse [@mediatingmisogyny; @trifiro].
-Despite the potential for the formation of new publics online, including issue publics driven by shared policy interests such as climate change, the leading voices in networked publics largely continue to be white, male, Christian, and have free time (often dictated by patriarchal norms) to actively contribute to discussions [@bruns2023; @mantilla2013; @degeus].
+Despite the potential for the formation of new publics online, including issue publics driven by shared policy interests such as climate change, the leading voices in networked publics largely continue to be white, male, Christian, and have free time (often dictated by patriarchal norms) to actively contribute to discussions [@bruns2023; @mantilla2013; @degeus; @tweetingclimate].
 Networked publics use trolling and harassment to undermine the authority of female politicians whose actions do not fit traditional gender roles and conceptions of power [@degeus; @mantilla2015; @megarry2014].
@@
 
-## Harassment of Women in Politics
+## Harassment of Women in Politics {.unnumbered}
 
@@
 
-## Data Collection
+## Data Collection {.unnumbered}
 
@@
 
-## Data Cleaning
+## Data Cleaning {.unnumbered}
 
-### Raw Data
+### Raw Data {.unnumbered}
 
@@
 
-### Coded Data
+### Coded Data {.unnumbered}
 
-After manually coding the 4,139 Tweets using my Codebook (see [Appendix]), I proceeded to the second round of cleaning.
+After manually coding the 4,139 Tweets using my Codebook, I proceeded to the second round of cleaning.
 I eliminated columns of data which were useful for determining the type of account but not relevant for the next steps of my analysis.
@@
 
-## Data Coding
+## Data Coding {.unnumbered}
 
@@
 There is agreement among scholars from fields such as communication and media studies, women and gender studies, and political science that there are no universal definition or ways of measuring and characterizing severity of harassment, incivility, and hate speech [@mantilla2015; @tenove; @krook2020].
-Through this study, I develop and test a new quantitative seven-point scale which contributes to on-going research by emphasizing everyday forms of harassment, such as microaggressions and questioning the authority of female politicians.
-My third category, Questioning authority, is a specific contribution, as it is a phenomenon recognized in the literature [@krook2020], but not typically included in coding schemes as a way to categorize harassment directed toward female politicians.
-
+Through this study, I develop and test a new quantitative seven-point scale which contributes to on-going research by emphasizing everyday forms of harassment, such as microaggressions and questioning the authority of female politicians [@krook2020].
+My third category, Questioning authority, is a specific contribution, as it is not typically included in coding schemes as a way to categorize harassment directed toward female politicians.
 These more everyday forms of harassment are often missed during binary coding conducted by large language models (LLMs).
@@
 
-To ensure intercoder reliability, an undergraduate research assistant coded a random selection of ten percent of the total number of Tweets in the sample.
+To ensure validity, an undergraduate research assistant coded a random selection of ten percent (413) of the total number of Tweets in the sample.
 Intercoder reliability was calculated using the package `irr` [@irr] to check the extended percentage agreement among coders.
-Agreement for severity of harassment was 87.5%, while agreement for type of account was 76%.
-@lacy2015 suggest that results over 80% are acceptable and results between 67% and 80% are tentatively acceptable, with explanation (further discussed in [Limitations]).
+Acceptable levels of agreement were reached, with agreement for severity of harassment at 87.5% and type of account at 76% [@lacy2015].
 
-## Data Limitations
+## Data Limitations {.unnumbered}
 
@@
 
-## Severity of Harassment
+## Severity of Harassment {.unnumbered}
 
@@
 
-## Type of Account
+## Type of Account {.unnumbered}
 
@@
 
-<!-- length(unique(finalized_cleaned_tweets$username)) While some users sent multiple replies to either one, two, or all of the female politicians, over 75% of users only appeared once in the dataset.
-My type of account results are consistent with the findings of @theocharis and @ward2020, who reveal that "...
-uncivil behavior seems to be common among many frustrated citizens who take to Twitter to angrily criticize and insult politicians" [@theocharis, p.
-9].
--->
-
 ```{r}
@@
 
-## Chrystia Freeland
+## Chrystia Freeland {.unnumbered}
 
@@
 
-## Elizabeth May
+## Elizabeth May {.unnumbered}
 
@@
 
-## Laurel Collins
+## Laurel Collins {.unnumbered}
 
@@
 
-## Elizabeth May
+## Elizabeth May {.unnumbered}
 The results for severity of harassment and type of accounts detected in MP May's sample of Tweets are largely consistent with my hypothesis, although there were slightly fewer Positive and Neutral Tweets than anticipated.
@@
 
-## Deliberative Democracy
+## Deliberative Democracy {.unnumbered}
 
@@
 
-## Limitations
+## Limitations {.unnumbered}
 
@@
 
-In this paper, I examined Tweets explicitly discussing climate change and environmental policy sent to DPM Freeland, MP May, and MP Collins to measure the severity of harassment on a seven-point scale and type of accounts behind the Tweets.
-My results reveal that over 85% of Tweets sent to the three politicians contained some level of harassment.
-My model identified and predicted nearly no quantitative differences between Tweets sent to all three female politicians.
-Spammer and Anonymous accounts were most frequently associated with engaging with the female politicians on Twitter and being responsible for sending the more serve forms of harassment identified.
-The Tweets analyzed for this study generally matched the criteria of what constitutes healthy democratic discourse, with users with multiple, diverse viewpoints weighing in on the issue of climate change.
+This study examines replies to Tweets explicitly discussing climate change and environmental policy sent to DPM Freeland, MP May, and MP Collins.
+My results from manually coding and my Bayesian hierarchical model suggest that the three politicians are equally impacted by harassment, with 86% of Tweets containing some form of harassment.
+Questioning authority and name-calling/gender insults were the most identified forms of harassment, while Spammers and Anonymous accounts were most frequently associated with sending harassing replies.
+This study contributes to our understanding of the online harassment of female politicians by developing a seven-point scale to measure more nuanced forms of harassment and a six-point scale to categorize the types of accounts behind the replies
+
+The Tweets analyzed for this study generally match the criteria of what constitutes healthy democratic discourse, with users with multiple, diverse viewpoints weighing in on the issue of climate change.
 It is crucial to ensure we continue studying and discussing the intersection of climate change denialism and misogyny, because if we cannot mediate the risks of gendertrolling at the highest echelons of power, then female politicians may self-censor and risk everyone's ability to engage in respectful discourse surrounding climate change [@mediatingmisogyny].

### 2024-02-09 Outputs/Paper/Publication_version/paper_for_pub.qmd
data and paper updates

@@
 title: "Torrential Twitter? Measuring the Severity of Harassment when Canadian Female Politicians Tweet about Climate Change"
-author: "Inessa De Angelis^[Faculty of Information, University of Toronto, Inessa.DeAngelis@mail.utoronto.ca]"
+author: "Inessa De Angelis^[Faculty of Information, University of Toronto, Inessa.DeAngelis@mail.utoronto.ca, Twitter: @inessadeangelis]"
 thanks: "Code and select data available at: https://github.com/InessaDeAngelis/torrential_twitter_bell_conf "
@@
 date-format: "long"
-abstract: "Research has shown that women in politics face considerable online harassment know as “gendertrolling.” This study investigates the severity of harassment three Canadian female politicians receive when Tweeting about climate change and the types of accounts behind the replies.
-All replies to climate and environmental focused Tweets posted by the politicians from September 2022 to October 2023 were collected for quantitative content analysis.
-Results from my content analysis reveal that 86% of Tweets contained some form of harassment.
-I then built a Bayesian hierarchical model to investigate the relationship between the severity of harassment and the type of account that a user has.
-The results from my model suggest that despite differences in political affiliation and status, the three politicians are equally impacted by harassment when Tweeting about climate change.
+abstract: "The online harassment of female politicians who focus on climate change and environmental policy has become a major problem in Canada and other democratic jurisdictions.
+Despite growing awareness of the problem, there is little agreement among scholars on how to measure these nuanced forms of harassment.
+This study develops an original seven-point scale to measure the severity of harassment three Canadian female politicians receive when Tweeting about climate change, and a six-point scale to categorize the types of accounts behind the replies.
+My results reveal that 86% of replies contained some form of harassment, most often name-calling or questioning the authority of the female politicians and come from users with spam or anonymous accounts.
+Further results from my Bayesian hierarchical model suggest that despite differences in status and political affiliation across the three politicians, they are almost equally impacted by harassment when Tweeting about climate change.
+These findings contribute to understanding the intersection between climate change denialism and the gendered nature of online harassment.
 *This paper contains language and themes that some readers may find offensive.*"
@@
 toc: true
-number-sections: true
+number-sections: false
 bibliography: publication_references.bib
@@
 
-My analysis reveals that 86% of all replies to Tweets about climate change and environmental policy that originated on the accounts of DPM Freeland, MP May, and MP Collins contain some form of harassment, ranging from Questioning authority to Hate speech.
+My analysis reveals that 86% of all replies to Tweets contain some form of harassment, ranging from Questioning authority to Hate speech.
 Questioning the authority of female politicians, followed by Name-calling/Gender insults were the most common forms of harassment identified, accounting for over 80% of all Tweets.
@@
 
-This study contributes to our knowledge of online harassment faced by female politicians by introducing a seven-point scale to measure the severity of harassment and a six-point scale to categorize the types of accounts behind the replies.
-The third category of harassment, questioning authority, is a specific contribution, as it is a phenomenon recognized in the literature [@krook2020], yet not typically included in coding schemes designed to measure harassment.
-Lastly, this study advances our understanding of the intersection between climate change denialism and online misogyny, revealing that the combination of the two areas is toxic for female politicians and democratic discourse.
+This study contributes to our knowledge of the online harassment faced by female politicians by introducing a seven-point scale to measure the severity of harassment and a six-point scale to categorize the types of accounts behind the replies.
+The third category of harassment, Questioning authority, is a specific contribution, as it is a phenomenon recognized in the literature [@krook2020], but not included in coding schemes designed to measure harassment.
+Lastly, this study advances our understanding of climate change denialism and online misogyny, revealing that the intersection of these two areas is toxic for female politicians and democratic discourse.
 
@@
 
-## Twitter & The Digital Public Sphere {.unnumbered}
+## Twitter & The Digital Public Sphere
 
@@
 
-## Harassment of Women in Politics {.unnumbered}
+## Harassment of Women in Politics
 
@@
 By employing the theory of deliberative democracy, this paper analyzes responses to Tweets sent by female politicians which explicitly discuss climate change and environmental policy to evaluate the extent at which they fulfill the characteristics of healthy democratic discourse.
-Often paired with their work on the public sphere, Jürgen Habermas and Richard Sennet are credited for publishing founding research on the theory of deliberative democracy [@kies2010].
 Recently, communication and media studies scholars have reconceptualized the formation of the public sphere, evaluating the role of platforms with promised democratizing qualities, disinformation, and how these mediums impact the original notion of deliberative democracy [@bruns2023].
@@
 23].
-Democratic legitimacy is established by allowing the public to collectively participate in respectful and reasonable deliberation about consequential decisions, while recognizing that there are multiple viewpoints on every issue [@masullochen; @pmc2019; @mckaytenove].
-@mckaytenove highlight that a new characteristic of deliberative democracy is the ability for those who participate in debate to do so in anonymous and pseudonymous ways, which both strengthen and undermine deliberation in different ways.
+Democratic legitimacy is established by allowing the public to collectively participate in respectful and reasonable deliberation about consequential decisions, while recognizing that there are multiple viewpoints on every issue [@pmc2019; @mckaytenove].
+@mckaytenove highlight that a new characteristic of deliberative democracy is the ability for those who participate in debate to do so in anonymous and pseudonymous ways, which both, in different ways, strengthens and undermines deliberation.
 
@@
 
-In this paper, I adopt a "to what extent" perspective.
+In this study, I adopt a "to what extent" perspective.
 This perspective aligns with the seven-point scale I developed to measure the severity of harassment on the basis that democratic discourse is nuanced and relies both on traditional democratic theory and contemporary approaches to media studies [@bruns2023].
@@
 
-## Data Collection {.unnumbered}
+## Data Collection
 
@@
 Only 6% of female MPs identify as a visible minority or Indigenous and do not frequently discuss climate change on Twitter, which is why my sample contains all white MPs [@hoc].
-Tweets also had to the contain the word "climate," "environment," and/or "environmental" (as part of the text of the Tweet or as a hashtag).
+Tweets also had to the contain the word "climate," "environment," and/or "environmental" (in text or as a hashtag).
 For threaded Tweets sent by the politicians, the first Tweet of the thread had to contain at least one of the key words and the overall focus of the thread had to be on climate change and/or environmental policy.
-For Tweet threads that mentioned one of the key words in later Tweets and in passing, these Tweets and replies were omitted due to their lack of relevance.
 Key words were also checked for applicability, given the use of words such as "climate" and "environment" to reference geopolitics and economic situations and not actual climate or environmental policy.
@@
 
-## Data Cleaning {.unnumbered}
+## Data Cleaning
 
-### Raw Data {.unnumbered}
+### Raw Data
 
-The raw datasets underwent multiple cleaning procedures and tests before being ready to manually code.
+The raw datasets underwent multiple cleaning procedures and tests in R before being ready to manually code.
 Cleaning refers to the process of preparing a raw dataset for further analysis, ensuring basic aspects like each Tweet and corresponding account metadata has its own column, row, and cell, before moving onto project-specific preparations [@tellingstories].
-Cleaning serves as a useful process for identifying anomalies in the dataset, such as mis-matched Tweets and account metadata.
 I eliminated columns of metadata unrelated to this study and focused on columns such as the text of the Tweet, the user's location, bio, profile picture, and whether they paid to be verified with a blue checkmark through Twitter's subscription program.
-All raw and coded data cleaning was done using R.
-The original Tweets and replies sent by the female politicians in response to their own thread (known as a threaded Tweet) were omitted during the cleaning process.
+The original Tweets and replies sent by the female politicians in response to their own threads were omitted during the cleaning process.
 The few replies sent in languages other than English, including French, Ukrainian, German, and Arabic were removed.
 Testing of the combined and cleaned datasets was conducted using `validate` [@validate] before being manually coded.
-The final number of Tweets left following these cleaning procedures are displayed in @tbl-breakdown, which highlights that DPM Freeland is overrepresented in my sample.
+The final number of Tweets left are displayed in @tbl-breakdown, which highlights that DPM Freeland is overrepresented in my sample.
 
@@
 
-### Coded Data {.unnumbered}
+### Coded Data
 
@@
 
-## Data Coding {.unnumbered}
+## Data Coding
 
@@
 Through this study, I develop and test a new quantitative seven-point scale which contributes to on-going research by emphasizing everyday forms of harassment, such as microaggressions and questioning the authority of female politicians [@krook2020].
-My third category, Questioning authority, is a specific contribution, as it is not typically included in coding schemes as a way to categorize harassment directed toward female politicians.
 These more everyday forms of harassment are often missed during binary coding conducted by large language models (LLMs).
-My seven-point scale also combines the nuance from previous qualitative projects which employ content analysis and interviews, while recognizing the benefits of more statistical and quantitative approaches offered by computational political communication researchers.
+My seven-point scale also combines the nuance from previous qualitative projects which employ content analysis and interviews, while recognizing the benefits of more statistical and quantitative approaches.
 
-To ensure validity, an undergraduate research assistant coded a random selection of ten percent (413) of the total number of Tweets in the sample.
-Intercoder reliability was calculated using the package `irr` [@irr] to check the extended percentage agreement among coders.
-Acceptable levels of agreement were reached, with agreement for severity of harassment at 87.5% and type of account at 76% [@lacy2015].
+To ensure validity, an undergraduate research assistant coded a random selection of 10% (413) of the total number of Tweets in the sample.
+Intercoder reliability was calculated using the R package `irr` [@irr] to check the extended percentage agreement among coders.
+Acceptable levels of agreement were reached, with agreement for severity of harassment at 88% and type of account at 76% [@lacy2015].
 
-## Data Limitations {.unnumbered}
+## Data Limitations
 
@@
 We are also limited by the information users choose to publicly display on their profiles, such as their location, so it is not always possible to confirm if an individual is Canadian or other identifying demographic information [@holmberg].
-Due to the global and open nature of social media platforms, some of the Tweets captured are from users who claim to be in the United States, the United Kingdom, and Australia, therefore limiting our ability to solely see the behaviours of Canadian users.
+Due to the global and open nature of social media platforms, some of the Tweets captured are from users who are in the United States, the United Kingdom, and Australia, therefore limiting our ability to solely see the behaviours of Canadian users.
 
@@
 
-## Severity of Harassment {.unnumbered}
+## Severity of Harassment
 
@@
 
-## Type of Account {.unnumbered}
+## Type of Account
 
@@
 
-## Chrystia Freeland {.unnumbered}
+## Chrystia Freeland
 
@@
 
-## Elizabeth May {.unnumbered}
+## Elizabeth May
 
@@
 
-## Laurel Collins {.unnumbered}
+## Laurel Collins
 
@@
 
-I am interested in seeing why some Twitter users are more predisposed than others to send harassing Tweets to Canadian female politicians.
-In particular, I want to further investigate the combination of the type of account a user has, whether they are verified, and which politician they are replying to in order to predict if they are more likely to send a harassing Tweet.
+This model investigates the combination of the type of account a user has, whether they are verified, and which politician they are replying to in order to predict if they are more likely to send a harassing Tweet.
 Historically, accounts with the blue checkmark/tick were regarded as credible individuals and/or organizations, sharing legitimate information [@unverified].
@@
 The results from the model suggest that despite differences in status and political affiliation across the three politicians, they are almost equally impacted by harassment on Twitter.
-Moreover, all types of accounts are predisposed to sending harassing Tweets, especially Professional accounts, which I did not hypothesize, but will be explained in my [Discussion] section.
+Moreover, all types of accounts are predisposed to sending harassing Tweets, especially Professional accounts, which will be explored in my [Discussion] section.
 
@@
 
-## Severity of Harassment {.unnumbered}
+## Severity of Harassment
 
-Based on my hypothesis, I expected that DPM Freeland, followed by MP May, then MP Collins would receive the most severe Tweets, however, MP Collins had more identified instances of Credible threats and Hate speech than MP May (for Hate speech, DPM Freeland had 29 instances, MP Collins had 2, and MP May had 1).
+It was anticipated that DPM Freeland, followed by MP May, then MP Collins would receive the most severe Tweets, however, MP Collins had more identified instances of Credible threats and Hate speech than MP May (for Hate speech, DPM Freeland had 29 instances, MP Collins had 2, and MP May had 1).
 I expected that everything of DPM Freeland's would be more severe -- with more identified instances of Hate speech and more Credible threats.
@@
 
-55% of Tweets fell under the Questioning authority category, which was ultimately higher than hypothesized (see @tbl-severity).
+55% of Tweets fell under the Questioning authority category, which was ultimately higher than expected (see @tbl-severity).
 As seen in @tbl-qa-example, Tweets which are categorized as Questioning authority differ from information-seeking questions because users intend to question the abilities of female politicians based on their political affiliation, gender, age, physical appearance, and corresponding assumed qualifications.
@@
 
-## Type of Account {.unnumbered}
-
-For the types of accounts, there were more Spammers and Anonymous accounts than I hypothesized, but these results align with previous research and our understanding of the increasingly toxic nature of Twitter [@phillips; @wagner; @theocharis].
+## Type of Account 
+Previous research and our understanding of the increasingly toxic nature of Twitter, support the high number of Spammers and Anonymous accounts identified [@phillips; @wagner; @theocharis].
 The high percentage of Anonymous accounts (37%) reinforces @mckaytenove's findings that anonymous (and often harassing) political speech is increasingly common in our contemporary era of deliberative democracy.
@@
 This subtle show of support for the Conservative Party is augmented by direct support for Conservative and right wing political movements in Canada and the United States by the use of words and phrases in user bios such as "#TrudeauMustGo," "#Pierre4PM," "#Trump2024," "MAGA," "CPC," "Conservative," and "PPC".
-288 unique users in my dataset explicitly identified themselves as having right-wing and ideological views, which supports my hypothesis.
+288 unique users in my dataset explicitly identified themselves as having right-wing and ideological views.
 
@@
 
-## Chrystia Freeland {.unnumbered}
+## Chrystia Freeland
 
-DPM Freeland's results for severity of harassment and type of account are largely consistent with my expectations and previous research into the harassment faced by eminent female politicians [@rheault].
+DPM Freeland's results for severity of harassment and type of account are largely consistent previous research into the harassment faced by eminent female politicians [@rheault].
 The use of memes, to undermine and harass DPM Freeland prominently features in her sample of Tweets.
@@
 Furthermore, at least one user in DPM Freeland's sample also stated their involvement in the far right online men’s rights movement called "men going their own way" (MGOW) [@maletears].
-These preliminary observations of qualitative far right behaviour are concerning for the future of democracy and the active participation of women in politics.
+These observations of qualitative far right behaviour are concerning for the future of democracy and the active participation of women in politics.
 
-## Elizabeth May {.unnumbered}
-The results for severity of harassment and type of accounts detected in MP May's sample of Tweets are largely consistent with my hypothesis, although there were slightly fewer Positive and Neutral Tweets than anticipated.
+## Elizabeth May 
+The results for severity of harassment and type of accounts detected in MP May's sample of Tweets are consistent with expectations, although there were slightly fewer Positive and Neutral Tweets than anticipated.
 55% of Tweets in MP May's sample were coded as Questioning authority, while 28% fall under the Name-calling/Gender insults category (see @tbl-liz_severity).
@@
 
-## Laurel Collins {.unnumbered}
+## Laurel Collins
 
-Tweets in MP Collins' sample, for both severity of harassment and type of account were generally more severe than I originally hypothesized.
+Tweets in MP Collins' sample, for both severity of harassment and type of account were generally more severe than hypothesized.
 I expected to see a fairly even split between Tweets coded as Questioning authority and Neutral, but ultimately 75% of Tweets were coded as Questioning authority and just 8% as Neutral (see @tbl-laurel_severity).
@@
 @tbl-mydear-example illustrates the use of patriarchal and paternalistic language directed toward MP Collins, with the use of "my dear".
-In addition to talking down the qualifications of MP Collins, this user also questions climate science (offering up the popular alternative science suggestion that arson is responsible for forest fires) and voting behaviours in British Columbia.
+In addition to talking down the qualifications of MP Collins, this user also questions her understanding of climate science and forest fires.
 Tweets like this one and others in MP Collins' sample continue to emphasize the microaggressions faced by female politicians as they communicate about consequential policy issues [@harmer; @mediatingmisogyny].
@@
 
-## Deliberative Democracy {.unnumbered}
+## Deliberative Democracy
 
-Of the three politicians, MP May's Twitter account best fulfills the definition of deliberative democracy previously outlined, having open conversations with multiple view points and two way flows of communication (despite 55% of her Tweets being coded as Questioning authority).
-All viewpoints, including both the fact Canada is not going far enough on climate action and is going too far (especially with carbon pricing) features prominently through the sample of Tweets.
+Of the three politicians, MP May's Twitter account best fulfills the definition of deliberative democracy previously outlined, having open conversations with multiple view points and two way flows of communication.
+All viewpoints, including the fact Canada is not going far enough on climate action and is going too far features prominently through the sample of Tweets.
 Among the users who believe and promote alternative facts, some claim climate change is simply changing weather, or that forest fires are caused by arson, or other niche reasons supported by user-generated websites.
@@
 MP Collins' networked public also possessed these characteristics, although she was less willing to engage by responding.
-DPM Freeland received significant amounts of verbal backlash and her staff intentionally did not response to replies from the public, meaning her Twitter account is more a space to broadcast political messages instead of engaging in open and constructive discourse with the public [@marland; @small2016].
-The lack of two-way discussion, possibly due to DPM Freeland's status and sheer volume of Tweets and replies from the public, makes the digital public sphere situated around her account unhealthy for democratic discourse.
-Although all three politicians could be using their Twitter accounts to more actively engage with the public, the waning engagement is understandable given Twitter's current state.
-Other more traditional means of two-way dialogue between elected officials and the public, such as town halls and constituent correspondence remain important ways to maintain deliberative democracy.
+DPM Freeland received significant amounts of verbal backlash and her staff intentionally did not response to replies from the public, meaning her Twitter account is a space to broadcast political messages instead of engaging in open and constructive discourse with the public [@marland].
+The lack of two-way discussion and continuous harassment, makes the digital public sphere situated around her account unhealthy for democratic discourse.
+Although all three politicians could be using their Twitter accounts to more actively engage with the public, it is important to ensure the continued use of more traditional means of two-way deliberative dialogue, including town hall meetings and email correspondence.
 
-## Limitations {.unnumbered}
+## Limitations
 
@@
 
-This study examines replies to Tweets explicitly discussing climate change and environmental policy sent to DPM Freeland, MP May, and MP Collins.
+This study examined replies to Tweets explicitly discussing climate change and environmental policy sent to DPM Freeland, MP May, and MP Collins.
 My results from manually coding and my Bayesian hierarchical model suggest that the three politicians are equally impacted by harassment, with 86% of Tweets containing some form of harassment.
-Questioning authority and name-calling/gender insults were the most identified forms of harassment, while Spammers and Anonymous accounts were most frequently associated with sending harassing replies.
+Questioning authority and Name-calling/Gender insults were the most identified forms of harassment, while Spammers and Anonymous accounts were most frequently associated with sending harassing replies.
 This study contributes to our understanding of the online harassment of female politicians by developing a seven-point scale to measure more nuanced forms of harassment and a six-point scale to categorize the types of accounts behind the replies
@@
 
-# Acknowledgments {.unnumbered}
+# Acknowledgments 
 The author(s) thank(s) Rohan Alexander for the helpful suggestions and feedback on drafts of this paper and Elizabeth Dubois for guidance during the early conception of this study.
@@
 
-# Funding {.unnumbered}
+# Funding 
 The author(s) disclose(s) receipt of the following financial support for the research, authorship, and/or publication of this article: This study was funded by the Social Sciences and Humanities Research Council of Canada (grant ID: 766-2022-0719) and the Government of Ontario, *2023-2024 Ontario Graduate Scholarship*.
 
-# Declaration of Conflicting Interests {.unnumbered}
+# Declaration of Conflicting Interests
 The author(s) declare(s) that there is no conflict of interest.

### 2024-02-09 Outputs/Paper/Publication_version/paper_for_pub.qmd
little fixes

@@
 title: "Torrential Twitter? Measuring the Severity of Harassment when Canadian Female Politicians Tweet about Climate Change"
-author: "Inessa De Angelis^[Faculty of Information, University of Toronto, Inessa.DeAngelis@mail.utoronto.ca, Twitter: @inessadeangelis]"
+author: "Inessa De Angelis^[Faculty of Information, University of Toronto, Inessa.DeAngelis@mail.utoronto.ca]"
 thanks: "Code and select data available at: https://github.com/InessaDeAngelis/torrential_twitter_bell_conf "
@@
 date-format: "long"
-abstract: "The online harassment of female politicians who focus on climate change and environmental policy has become a major problem in Canada and other democratic jurisdictions.
+abstract: "The online harassment of female politicians who focus on climate change and environmental policy has become a major problem in Canada and other democratic nations.
 Despite growing awareness of the problem, there is little agreement among scholars on how to measure these nuanced forms of harassment.

### 2024-02-12 Outputs/Paper/Publication_version/paper_for_pub.qmd
update

@@
 Tweets were coded using a seven-point scale to measure the severity of harassment and a six-point scale to categorize the types of accounts behind the replies.
-I then built a Bayesian hierarchical model to explore the relationship between the type of account, whether a user was verified through Twitter's subscription program, and which female politician the reply was directed toward to see whether certain combinations of these variables are more likely to lead to a harassing reply.
+I then built a Bayesian hierarchical model to explore the relationship between the type of account, whether a user was verified through Twitter's subscription program, and which female politician the reply was directed toward, to see whether certain combinations of these variables are more likely to lead to a harassing reply.
 
@@
 Although Jürgen Habermas wrote about the public sphere in the mid-twentieth century, eighteenth century bourgeois society served as the basis for his theory, overlooking how elites tried to influence and dominate the form political discourse took among other socio-economic classes [@mediatingmisogyny; @megarry2014].
-Through Habermas' conceptualization, the public sphere intends to magnify the voices of the political elites (traditionally white men), while diminishing and even vilifying the voices of minorities -- traits which have been transposed into the digital public sphere [@mediatingmisogyny].
+Through Habermas' conceptualization, the public sphere tends to magnify the voices of the political elites (traditionally white men), while diminishing and even vilifying the voices of minorities -- traits which have been transposed into the digital public sphere [@mediatingmisogyny].
 
@@
 Discourse traditionally happened in mediated spaces, but the rise of social media allows it to happen everywhere, theoretically breaking down barriers of who has access to the walled garden of democratic discourse [@mediatingmisogyny; @trifiro].
-Despite the potential for the formation of new publics online, including issue publics driven by shared policy interests such as climate change, the leading voices in networked publics largely continue to be white, male, Christian, and have free time (often dictated by patriarchal norms) to actively contribute to discussions [@bruns2023; @mantilla2013; @degeus; @tweetingclimate].
+Despite the potential for the formation of new publics online, including issue-specific publics driven by shared policy interests such as climate change, the leading voices in networked publics largely continue to be white, male, Christian, and have free time (often dictated by patriarchal norms) to actively contribute to discussions [@bruns2023; @mantilla2013; @degeus; @tweetingclimate].
 Networked publics use trolling and harassment to undermine the authority of female politicians whose actions do not fit traditional gender roles and conceptions of power [@degeus; @mantilla2015; @megarry2014].
-Consequently, women have and continue to be on the margins of the public sphere, both in physical spaces like the House of Commons and online, as underscored by an @ipu global survey which found that 82% of female politicians reported being subjected to psychological violence (including harassment, threats, and sexist comments).
+Consequently, women have and continue to be on the margins of the public sphere, both in physical spaces like the House of Commons and online.
+This is underscored by an @ipu global survey which found that 82% of female politicians reported being subjected to psychological violence (including harassment, threats, and sexist comments).
 In Canada, specific examples of on-going marginalization can be seen through the lived experiences of women in politics, with only one female Prime Minister to date (the Rt.
 Hon.
-Kim Campbell) and 30% of federal MPs being female [@degeus; @hoc].
+Kim Campbell) and only 30% of federal MPs being female [@degeus; @hoc].
 
@@
 The behaviours and norms of the Wild West continue to play out through the actions of male tech CEOs, such as Elon Musk, and through the way platforms are governed.
-While often lacking in application, social media platforms including Twitter have slowly adopted rigorous content moderation and community safety policies [@overtime].
+While often lacking in application, social media platforms including Twitter have tended to slowly adopt rigorous content moderation and community safety policies [@overtime].
 
@@
 Some scholars view the theory in rigid terms, evaluating all characteristics and scenarios, such as political parties, systems, and institutions on a "yes" or "no" basis [@sokolon].
-However, as @rossini suggests, the theory of deliberative democracy can be viewed on a scale -- looking at the extent in which healthy democratic speech exists in specific contexts.
+However, as @rossini suggests, the theory of deliberative democracy can be viewed on a scale -- looking at the extent to which healthy democratic speech exists in specific contexts.
 In our increasingly digitized democracy, we cannot overlook or discount how algorithms and platform affordances are building the networks and contexts in which influential democratic deliberation takes place [@bruns2023].
@@
 
-All Twitter data was collected throughout the month of October 2023 using the statistical programming software R [@r] and functions from `voson.tcn` [@gertzel2021] and the `tidyverse` [@rTidyverse].
+All Twitter data was collected using the statistical programming software R [@r] and functions from `voson.tcn` [@gertzel2021] and the `tidyverse` [@rTidyverse].
 Paid access to Twitter's Basic v2 Application Programming Interface (API) endpoint was obtained before using the advanced search feature to determine which Tweets I wanted to download via the API.
@@
 These three politicians were selected based on their pro-climate change stances, evidence of harassing Tweets, and diversity in regional representation and political affiliation.
-Only 6% of female MPs identify as a visible minority or Indigenous and do not frequently discuss climate change on Twitter, which is why my sample contains all white MPs [@hoc].
+Only 6% of female MPs identify as a visible minority or Indigenous and do not frequently discuss climate change on Twitter, which is why my sample contains only white MPs [@hoc].
 Tweets also had to the contain the word "climate," "environment," and/or "environmental" (in text or as a hashtag).
@@
 Key words were also checked for applicability, given the use of words such as "climate" and "environment" to reference geopolitics and economic situations and not actual climate or environmental policy.
-Within the parameters of the sample, DPM Freeland's Tweets were from October 2022 to October 2023 and had either the key word "climate" or "environment".
-MP May's Tweets were from September 2022 to October 2023 and included the words "climate," "environment," and "environmental".
-Lastly, MP Collins' Tweets were from October 2022 to October 2023 and included the words "climate," "environment," and "environmental."
+Within the parameters of the sample, all Tweets were from September 2022 to October 2023.
+DPM Freeland's Tweets had either the key word "climate" or "environment." MP May and MP Collins' Tweets included the words "climate," "environment," and "environmental."
 
@@
 Intercoder reliability was calculated using the R package `irr` [@irr] to check the extended percentage agreement among coders.
-Acceptable levels of agreement were reached, with agreement for severity of harassment at 88% and type of account at 76% [@lacy2015].
+Acceptable levels of agreement were reached according to @lacy2015, with agreement for severity of harassment at 88% and type of account at 76%.
 
@@
 Bayesian hierarchical modeling using the statistical programming language R [@r], employing `rstanarm` [@rstanarm], `marginaleffects` [@marginal], and `modelsummary` [@modelsummary] can help predict and further investigate this relationship.
-The model was fit in a Bayesian framework using `rstanarm` [@rstanarm].
+The model was fit using `rstanarm` [@rstanarm].
 For the priors, I followed the standard weakly informed prior distributions by using the normal definition with mean 0 and standard deviation 2.5 as used in the `rstanarm` package.
@@
   labs(
-    x = "Harassment",
-    y = "Estimated probability that a Tweet contains harassment",
+    x = "Contains Harassment",
+    y = "Estimated probability that a Tweet \ncontains harassment",
     color = "Name of Politician"
@@
   theme_classic() +
-  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 8)) + 
-  theme(axis.text.y = element_text(size = 8)) + 
-  theme(axis.title.y = element_text(size = 8)) +
+  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 10)) + 
+  theme(axis.text.y = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(size = 10)) +
+  theme(axis.title.y = element_text(size = 12)) +
+  theme(axis.title.x = element_text(size = 12)) +
   theme(legend.position = "bottom") +
@@
 # Acknowledgments 
-The author(s) thank(s) Rohan Alexander for the helpful suggestions and feedback on drafts of this paper and Elizabeth Dubois for guidance during the early conception of this study.
-The author(s) also thank(s) Sarah Xie and Allyson Cui for their research assistance.
+The author thanks Rohan Alexander for the helpful suggestions and feedback on drafts of this paper and Elizabeth Dubois for guidance during the early conception of this study.
+The author also thanks Sarah Xie and Allyson Cui for their research assistance.
 
 # Funding 
-The author(s) disclose(s) receipt of the following financial support for the research, authorship, and/or publication of this article: This study was funded by the Social Sciences and Humanities Research Council of Canada (grant ID: 766-2022-0719) and the Government of Ontario, *2023-2024 Ontario Graduate Scholarship*.
+The authors discloses receipt of the following financial support for the research, authorship, and/or publication of this article: This study was funded by the Social Sciences and Humanities Research Council of Canada (grant ID: 766-2022-0719) and the Government of Ontario, *2023-2024 Ontario Graduate Scholarship*.
 
 # Declaration of Conflicting Interests
-The author(s) declare(s) that there is no conflict of interest.
+The author declares that there is no conflict of interest.
 

### 2024-02-12 Outputs/Paper/Publication_version/paper_for_pub.qmd
repo update

@@
 author: "Inessa De Angelis^[Faculty of Information, University of Toronto, Inessa.DeAngelis@mail.utoronto.ca]"
-thanks: "Code and select data available at: https://github.com/InessaDeAngelis/torrential_twitter_bell_conf "
+thanks: "Code and select data available at: https://github.com/InessaDeAngelis/Torrential_Twitter_Paper "
 date: "today"

### 2024-02-14 Outputs/Paper/Publication_version/paper_for_pub.qmd
tinkering

@@
 
-Gender-based harassment and gendertrolling on Twitter is well-documented in the literature [@mediatingmisogyny; @carlson; @trifiro; @mantilla2013].
+Gender-based harassment and gendertrolling on Twitter is well documented in the literature [@mediatingmisogyny; @carlson; @trifiro; @mantilla2013].
 Previous research has started distinguishing traits of harassment based on a politician's status and visibility in politics and across traditional and social media.
@@
 Both  @collignon2020 and @erikson found that the intersection between a politician's age, gender, and political affiliation largely determines the type and frequency of harassment they face, leading to younger, female politicians more frequently receiving harassing messages than older politicians.
+Female politicians of color, often face more harassment than any other group [@mediatingmisogyny].
 Widespread and systematic harassment threatens meaningful political participation by women, the nature of policy debates in the House of Commons, and the future of democracy [@southern; @degeus].
@@
     booktabs = TRUE,
+    linesep = ""
   )
@@
 
+# This code fixed the gap issue! https://stackoverflow.com/questions/67365583/extra-white-space-after-knitting-in-rmarkdown
+
 finalized_cleaned_tweets |>
@@
     booktabs = TRUE,
+    linesep = "" 
   ) 
@@
     booktabs = TRUE,
+    linesep = ""
   ) 
@@
 For the priors, I followed the standard weakly informed prior distributions by using the normal definition with mean 0 and standard deviation 2.5 as used in the `rstanarm` package.
+The model is:
 
@@
 \end{aligned}
-$$ Where $y_i$ is whether a Tweet contained harassment, $\pi_i = \mbox{Pr}(y_i=1)$, and $\alpha^{\mbox{account}}$, $\alpha^{\mbox{politician}}$, and $\alpha^{\mbox{verified}}$ and are the effect of the type of account a user has, which politician they are replying to, and whether their account is verified.
+$$ Where $y_i$ is whether a Tweet contained harassment, $\pi_i = \mbox{Pr}(y_i=1)$, and $\alpha^{\mbox{account}}$, $\alpha^{\mbox{politician}}$, and $\alpha^{\mbox{verified}}$ are the effect of the type of account a user has, which politician they are replying to, and whether their account is verified.
 The $a[i]$, $p[i]$, and $v[i]$ refer to which type of account, which politician, and whether a user is verified.
 $A$, $P$, and $V$ are the total number of types of accounts, politicians, and verification options, respectively.
-The binary response variable, called `harassment_binary`, has a value of 0 if a Tweet does not contain harassment and a value of 1 if it contains harassment.
 The Positive and Neutral categories on my seven-point scale make up the value of 0 and all remaining categories (Questioning authority through Hate speech) make up the value of 1.
+The binary response variable, $y_i$, is called `harassment_binary` and has a value of 0 if a Tweet does not contain harassment and a value of 1 if it contains harassment.
 
@@
 ```
-@tbl-modsummary presents the estimates generated by the model. For ease of analysis, @tbl-marginal displays the estimates as predictions in a table and @fig-plotted shows the predictions graphed.
+@tbl-modsummary presents the estimates generated by the model. For ease of analysis, @tbl-marginal displays the estimates as predictions in a table and @fig-plotted2 shows the predictions graphed.
 
@@
     col.names = c("Term", "Contrast", "Estimate"),
-    digits = 2, booktabs = TRUE
+    digits = 2, 
+    booktabs = TRUE,
+    linesep = ""
   )
@@
 #| eval: true
-#| label: fig-plotted
+#| label: fig-plotted2
 #| fig-cap: Predicting whether a Tweet contains harassment or not, on the basis of the type of account behind the Tweet, which politician the Tweet was in response to, and whether a user is verified.
@@
 
-harassment_model_predictions |>
-  ggplot(aes(x = harassment_binary, y = estimate, color = name_of_politician)) +
-  geom_jitter(width = 0.2, height = 0.0, alpha = 0.3) +
+ggplot(harassment_model_predictions, aes(verified, estimate)) +
+  geom_jitter(aes(colour = factor(name_of_politician))) +
+  facet_wrap(harassment_binary ~type_of_account) +
   labs(
-    x = "Contains Harassment",
-    y = "Estimated probability that a Tweet \ncontains harassment",
+    x = "Whether an account is verified",
+    y = "Estimated probability that a \nTweet contains harassment",
     color = "Name of Politician"
   ) +
-  theme_classic() +
-  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 10)) + 
-  theme(axis.text.y = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(size = 10)) +
-  theme(axis.title.y = element_text(size = 12)) +
-  theme(axis.title.x = element_text(size = 12)) +
   theme(legend.position = "bottom") +
-  theme(legend.text = element_text(size = 6)) +
-  theme(legend.title = element_text(size = 9))
+  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 7)) +
+  theme(axis.text.y = element_text(size = 7)) + 
+  scale_colour_manual(values = c("darkblue", "darkcyan", "yellow"))
 
@@
 
-DPM Freeland's results for severity of harassment and type of account are largely consistent previous research into the harassment faced by eminent female politicians [@rheault].
+DPM Freeland's results for severity of harassment and type of account are largely consistent with previous research into the harassment faced by eminent female politicians [@rheault].
 The use of memes, to undermine and harass DPM Freeland prominently features in her sample of Tweets.
@@
 # Funding 
-The authors discloses receipt of the following financial support for the research, authorship, and/or publication of this article: This study was funded by the Social Sciences and Humanities Research Council of Canada (grant ID: 766-2022-0719) and the Government of Ontario, *2023-2024 Ontario Graduate Scholarship*.
+The author discloses receipt of the following financial support for the research, authorship, and/or publication of this article: This study was funded in part by the Social Sciences and Humanities Research Council of Canada (grant ID: 766-2022-0719) and the Government of Ontario, *2023-2024 Ontario Graduate Scholarship*.
 

### 2024-02-14 Outputs/Paper/Publication_version/paper_for_pub.qmd
final edits

@@
 Key words were also checked for applicability, given the use of words such as "climate" and "environment" to reference geopolitics and economic situations and not actual climate or environmental policy.
-Within the parameters of the sample, all Tweets were from September 2022 to October 2023.
 DPM Freeland's Tweets had either the key word "climate" or "environment." MP May and MP Collins' Tweets included the words "climate," "environment," and "environmental."
@@
 
-ggplot(harassment_model_predictions, aes(verified, estimate)) +
+ggplot(harassment_model_predictions, aes(harassment_binary, estimate)) +
   geom_jitter(aes(colour = factor(name_of_politician))) +
-  facet_wrap(harassment_binary ~type_of_account) +
+  facet_wrap(verified ~type_of_account) +
   labs(
-    x = "Whether an account is verified",
+    x = "Whether a Tweet contains harassment",
     y = "Estimated probability that a \nTweet contains harassment",
@@
   theme(axis.text.x = element_text(angle=45, hjust = 1, size = 7)) +
-  theme(axis.text.y = element_text(size = 7)) + 
+  theme(axis.text.y = element_text(size = 6)) + 
   scale_colour_manual(values = c("darkblue", "darkcyan", "yellow"))

### 2024-02-14 Scripts/07-intercoder_prep.R

@@ -1,0 +1,525 @@
+#### Preamble ####
+# Purpose: Preps dataset for additional coders
+# Author: Inessa De Angelis
+# Date: 10 January 2024
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites
+  # All scripts to download, clean, and test raw Tweets
+
+#### Workspace setup ####
+library(tidyverse)
+library(janitor)
+
+## Read in datasets ##
+# Chrystia #
+final_cleaned_chrystia_tweets <- read_csv("Outputs/Data/Chrystia/final_cleaned_chrystia_tweets_update.csv")
+show_col_types = FALSE
+
+# Elizabeth #
+final_cleaned_liz_tweets <- read_csv("Outputs/Data/Elizabeth/final_cleaned_liz_tweets.csv")
+show_col_types = FALSE
+
+# Laurel
+final_cleaned_laurel_tweets <- read_csv("Outputs/Data/Laurel/final_cleaned_laurel_tweets.csv")
+show_col_types = FALSE
+
+#### Cleaning and prep ####
+## Clean names ##
+# Chrystia #
+final_cleaned_chrystia_tweets =
+  clean_names(final_cleaned_chrystia_tweets)
+
+# Elizabeth #
+final_cleaned_liz_tweets =
+  clean_names(final_cleaned_liz_tweets)
+
+# Laurel #
+final_cleaned_laurel_tweets =
+  clean_names(final_cleaned_laurel_tweets)
+
+## Add politician name column ##
+# Chrystia #
+final_cleaned_chrystia_tweets1 =
+  final_cleaned_chrystia_tweets |>
+  mutate(name_of_politician = c("Chrystia Freeland"),
+         .before = name) |>
+  select(name_of_politician, name, verified, url, followers, following, bio, username, profile_picture, location, text, user_id, conversation_id)
+head(final_cleaned_chrystia_tweets1)
+
+# Elizabeth #
+final_cleaned_liz_tweets1 =
+  final_cleaned_liz_tweets |>
+  mutate(name_of_politician = c("Elizabeth May"),
+         .before = name) |>
+  select(name_of_politician, name, verified, url, followers, following, bio, username, profile_picture, location, text, user_id, conversation_id)
+head(final_cleaned_liz_tweets1)
+
+# Laurel #
+final_cleaned_laurel_tweets1 =
+  final_cleaned_laurel_tweets |>
+  mutate(name_of_politician = c("Laurel Collins"),
[…]

### 2024-02-14 Scripts/08-intercoder_tests.R

@@ -1,0 +1,248 @@
+#### Preamble ####
+# Purpose: Measures intercoder reliability
+# Author: Inessa De Angelis
+# Date: 10 January 2024
+# Contact: inessa.deangelis@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites
+  # 07-intercoder_prep.R
+# CODE from: https://bookdown.org/content/759d32f5-0f3a-4e44-b515-a0a8cfaba221/tutorial-6-data-collection-testing-intercoder-reliability.html
+
+#### Workspace setup ####
+library(tidyverse)
+library(janitor)
+library(irr)
+
+#### Read in three coders' data ####
+# Coder 1
+inessa_tweets <- read_csv("Outputs/Data/intercoder/inessa_tweets.csv")
+show_col_types = FALSE
+
+# Code 2
+sarah_tweets <- read_csv("Outputs/Data/intercoder/sarah_tweets.csv")
+show_col_types = FALSE
+
+# Coder 3
+allyson_tweets <- read_csv("Outputs/Data/intercoder/allyson_tweets.csv")
+show_col_types = FALSE
+
+#### Data cleaning and dataset standardization ####
+## Name organization ##
+# Coder 2
+cleaned_sarah_tweets <-
+  clean_names(sarah_tweets)
+
+# Coder 3 
+cleaned_allyson_tweets <-
+  clean_names(allyson_tweets)
+
+## Select columns ##
+# Coder 1
+cleaned_inessa_tweets <-
+  inessa_tweets |>
+  select(
+    name_of_politician,
+    username,
+    tweet_text,
+    severity_of_harassment,
+    type_of_account
+  )
+head(cleaned_inessa_tweets)
+
+# Coder 2 
+cleaned_sarah_tweets <-
+  cleaned_sarah_tweets |>
+  select(
+    coder_name,
+    name_of_politician,
+    username,
+    tweet_text,
+    severity_of_harassment,
+    type_of_account
+  )
+head(cleaned_sarah_tweets)  
+
+# Coder 3
+cleaned_allyson_tweets <-
+  cleaned_allyson_tweets |>
+  select(
+    coder_name,
+    name_of_politician,
+    username,
+    tweet_text,
+    severity_of_harassment,
+    type_of_account
+  )
+head(cleaned_allyson_tweets)  
+
+## Manipulate columns ##
+# Add coder_name for Coder 1
+finalized_inessa_tweets <-
[…]

### 2024-02-15 Outputs/Paper/Publication_version/paper_for_pub.qmd
minor updates

@@
   ) +
+  theme_bw() +
   theme(legend.position = "bottom") +
